---
title: "🌊 Visual Analysis Finding 🪸"
format:
  html:
    mermaid: 
      theme: default
    
execute:
  warning: false
  freeze: false
  
code-fold: false
---

```{r}
#| echo: false
pacman::p_load(jsonlite, tidyverse, ggtext,   
               knitr, lubridate, hms, scales,   
               tidytext, tm, SnowballC,   
               patchwork, ggraph,    
               tidygraph, igraph, ggiraph,    
               SmartEDA, plotly, wordcloud,    
               ggh4x, visNetwork, RColorBrewer, 
               circlize, ggalluvial, reactable)  
```

```{r}
#| echo: false
mc3_data <- fromJSON("data/mc3_graph.json")
mc3_schema <- fromJSON("data/MC3_schema.json")
```

```{r}
#| echo: false
node_legend_colors_plot <- c(
  "Person" = "#88CCEE",
  "Vessel" = "#D55E00",
  "Organization" = "#117733",
  "Location" = "#AA4499",
  "Group"= "#CC79A7",
  "Event" = "#DDCC77",
  "Relationship" = "#AF8DC3",
  "Nadia Conti" = "red"
)

node_legend_shapes_plot <- c(
  "Person" = "dot",
  "Vessel" = "triangle",
  "Organization" = "square",
  "Location" = "diamond",
  "Group" = "circle plus",
  "Event" = "star",
  "Relationship" = "square x",
  "Nadia Conti" = "star"
)

STYLES <- list(
  node_label_dark = "black",
  font_family = "Roboto Condensed"
)
```

```{r}
#| echo: false
mc3_nodes_raw <- as_tibble(mc3_data$nodes)
mc3_edges_raw <- as_tibble(mc3_data$edges)
```

```{r}
#| echo: false
#| output: false

library(ggplot2)

# Run ExpCatViz once at the top to avoid recomputing
ExpCatViz(data=mc3_nodes_raw,
          col="navyblue")

```

```{r}
#| echo: false
#| output: false
# Step 1: Count and reorder
mc3_nodes_ordered <- mc3_nodes_raw %>%
  count(sub_type) %>%
  arrange((n)) %>%
  mutate(sub_type = factor(sub_type, levels = sub_type))

# Step 2: Plot with navy bars, sorted, and horizontal
ggplot(mc3_nodes_ordered, aes(x = sub_type, y = n)) +
  geom_col(fill = "navy") +
  coord_flip() +
  labs(x = "Sub_type", y = "Count",
    title = "Distribution of Subtypes") +
  theme_minimal()
```

```{r}
#| echo: false
#| output: false
# Step 1: Filter for type == "Entity", count sub_type, sort 
relationship_subtypes <- mc3_nodes_raw %>%
  filter(type == "Entity") %>%
  count(sub_type) %>%
  arrange(n) %>%
  mutate(sub_type = factor(sub_type, levels = sub_type)) 

# Step 2: Plot
ggplot(relationship_subtypes, aes(x = sub_type, y = n)) +
  geom_col(fill = "navy") +
  coord_flip() +
  labs(
    x = "Entity Subtype",
    y = "Count",
    title = "Distribution of Entity Subtypes"
  ) +
  theme_minimal()
```

```{r}
#| echo: false
#| output: false
# Step 1: Filter for type == "Event", count sub_type, sort 
relationship_subtypes <- mc3_nodes_raw %>%
  filter(type == "Event") %>%
  count(sub_type) %>%
  arrange(n) %>%
  mutate(sub_type = factor(sub_type, levels = sub_type)) 

# Step 2: Plot
ggplot(relationship_subtypes, aes(x = sub_type, y = n)) +
  geom_col(fill = "navy") +
  coord_flip() +
  labs(
    x = "Event Subtype",
    y = "Count",
    title = "Distribution of Event Subtypes"
  ) +
  theme_minimal()
```

```{r}
#| echo: false
#| output: false
# Step 1: Filter for type == "Relationship", count sub_type, sort 
relationship_subtypes <- mc3_nodes_raw %>%
  filter(type == "Relationship") %>%
  count(sub_type) %>%
  arrange(n) %>%
  mutate(sub_type = factor(sub_type, levels = sub_type))

# Step 2: Plot
ggplot(relationship_subtypes, aes(x = sub_type, y = n)) +
  geom_col(fill = "navy") +
  coord_flip() +
  labs(
    x = "Relationship Subtype",
    y = "Count",
    title = "Distribution of Relationship Subtypes"
  ) +
  theme_minimal()
```

```{r}
#| echo: false
#| output: false
ExpCatViz(data=mc3_edges_raw,
          col="navyblue")
```

```{r}
#| echo: false
#| output: false
# Step 1: Filter for type == "sent"
filtered_edges <- mc3_edges_raw %>%
  filter(type == "sent") %>%
  count(source) %>%
  arrange(desc(n)) %>%
  mutate(source = factor(source, levels = rev(unique(source))))  # descending 

# Step 2: Plot
ggplot(filtered_edges, aes(x = source, y = n)) +
  geom_col(fill = "navy") +
  coord_flip() +
  labs(
    title = "Distribution of 'sent' Edges type by Source",
    x = "Source",
    y = "Count"
  ) +
  theme_minimal()
```

```{r}
#| echo: false
mc3_nodes_cleaned <- mc3_nodes_raw %>%
  mutate(id = as.character(id)) %>%
  filter(!is.na(id)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-thing_collected, -time, -date, -friendship_type)
```

```{r}
#| echo: false
#| output: false
# Find the number of unique types in each column and sort descending
unique_counts <- mc3_nodes_cleaned %>%
  summarise_all(n_distinct) %>%
  pivot_longer(cols = everything(), names_to = "column", values_to = "unique_count") %>%
  arrange(desc(unique_count))  # sort by unique_count in descending order

# Print the result
print(unique_counts)
```

```{r}
#| echo: false
#| output: false
mc3_edges_cleaned <- mc3_edges_raw %>%
  rename(from_id = source,
         to_id = target) %>%
  mutate(across(c(from_id, to_id), as.character)) %>%
  # Parse to_id to get supertype and sub_type for target nodes (e.g., Event_Communication)
  separate(to_id, into = c("to_id_supertype", "to_id_sub_type", "to_id_num"),
           sep = "_", remove = FALSE, fill = "right", extra = "merge") %>%
  # Filter to ensure from_id and to_id exist in mc3_nodes_cleaned (prevent orphaned edges)
  filter(from_id %in% mc3_nodes_cleaned$id,
         to_id %in% mc3_nodes_cleaned$id) %>%
  filter(!is.na(from_id), !is.na(to_id))

print("Columns in mc3_edges_cleaned after initial cleaning:")
print(colnames(mc3_edges_cleaned))
print("Head of mc3_edges_cleaned after initial cleaning:")
print(head(mc3_edges_cleaned))

```

```{r}
#| echo: false
#| output: false
# Find the number of unique types in each column
unique_counts <- mc3_edges_cleaned %>%
  summarise_all(n_distinct) %>%
  pivot_longer(cols = everything(), names_to = "column", values_to = "unique_count")

# Print the unique counts for each column
print(unique_counts)
```

```{r}
#| echo: false
node_index_lookup <- mc3_nodes_cleaned %>%
  mutate(.row_id = row_number()) %>%
  select(id, .row_id)
```

```{r}
#| echo: false
mc3_edges_indexed <- mc3_edges_cleaned %>%
  left_join(node_index_lookup, by = c("from_id" = "id")) %>%
  rename(from = .row_id) %>%
  left_join(node_index_lookup, by = c("to_id" = "id")) %>%
  rename(to = .row_id) %>%
  # Filter out edges where either source or target node was not found
  filter(!is.na(from) & !is.na(to)) %>%
  # Select all columns to carry forward to mc3_edges_final
  select(from, to, id, is_inferred, type, # Original edge attributes
         from_id, to_id, to_id_supertype, to_id_sub_type, to_id_num # Original IDs and parsed target type
         )
```

```{r}
#| echo: false
used_node_indices <- sort(unique(c(mc3_edges_indexed$from, mc3_edges_indexed$to)))
mc3_nodes_final <- mc3_nodes_cleaned %>%
  slice(used_node_indices) %>%
  mutate(new_index = row_number())
```

```{r}
#| echo: false
old_to_new_index <- tibble(
  old_index = used_node_indices,
  new_index = seq_along(used_node_indices)
)
```

```{r}
#| echo: false
mc3_edges_final <- mc3_edges_indexed %>%
  left_join(old_to_new_index, by = c("from" = "old_index")) %>%
  rename(from_new = new_index) %>%
  left_join(old_to_new_index, by = c("to" = "old_index")) %>%
  rename(to_new = new_index) %>%
  # Explicitly select all columns that are needed downstream
  select(from = from_new, to = to_new,
         id, is_inferred, type,
         from_id, to_id, to_id_supertype, to_id_sub_type, to_id_num)
```

```{r}
#| echo: false
mc3_graph <- tbl_graph(
  nodes = mc3_nodes_final,
  edges = mc3_edges_final,
  directed = TRUE
)
```

```{r}
#| echo: false
#| output: false
# ---- 1. Define styles and legends ----

event_subtypes <- c(
  "Communication", "Monitoring", "VesselMovement", "Assessment",
  "Collaborate", "Endorsement", "TourActivity", "TransponderPing",
  "Harbor Report", "Fishing", "Criticize"
)

relationship_subtypes <- c(
  "Coordinates", "AccessPermission", "Operates", "Colleagues",
  "Suspicious", "Reports", "Jurisdiction", "Unfriendly", "Friends"
)

node_legend_colors_plot <- c(
  "Person" = "#88CCEE",
  "Vessel" = "#D55E00",
  "Organization" = "#117733",
  "Location" = "#AA4499",
  "Group"= "#CC79A7",
  "Event" = "#DDCC77",         # type level
  "Relationship" = "#AF8DC3"   # type level
)

node_legend_shapes_plot <- c(
  "Person" = "dot",
  "Vessel" = "triangle",
  "Organization" = "square",
  "Location" = "diamond",
  "Group" = "circle plus",
  "Event" = "star",              # type level
  "Relationship" = "square x"    # type level
)

STYLES <- list(
  node_label_dark = "black",
  font_family = "Roboto Condensed"
)

# ---- 2. Prepare nodes ----
nodes <- mc3_nodes_final %>%
  mutate(
    label = ifelse(is.na(name), id, name),
    
    # These parts are for pulling the related data from other fields
    tooltip_extra = case_when(
      type == "Event" & sub_type == "Communication" ~ content,
      type == "Event" & sub_type == "Monitoring" ~ findings,
      type == "Event" & sub_type == "VesselMovement" ~ destination,
      type == "Event" & sub_type == "Assessment" ~ results,
      type == "Relationship" & sub_type == "Coordinates" ~ coordination_type,
      type == "Relationship" & sub_type == "Operates" ~ operational_role,
      type == "Relationship" & sub_type == "Jurisdiction" ~ jurisdiction_type,
      TRUE ~ NA_character_
    ),
    
    title = paste0(
      "<b>", label, "</b><br>",
      "Type: ", type, "<br>",
      "Sub-type: ", sub_type, "<br>",
      ifelse(!is.na(tooltip_extra), paste0("<br><b>Details:</b> ", tooltip_extra), "")
    ),
    
    # Fallback logic: if sub_type is NA or not in styling list, use type instead
    group = ifelse(sub_type %in% names(node_legend_colors_plot), sub_type, type)
  ) %>%
  select(id, label, group, title) %>%
  distinct()

# ---- 3. Prepare directed edges (type == "sent") ----

edges <- mc3_edges_final %>%
  filter(from_id %in% nodes$id & to_id %in% nodes$id) %>%
  select(from = from_id, to = to_id)

# ---- 4. Build visNetwork ----

net <- visNetwork(nodes, edges, width = "100%", height = "600px") %>%
  visEdges(arrows = list(to = list(enabled = TRUE, scaleFactor = 1.5))) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visNodes(font = list(
    size = 14,
    color = STYLES$node_label_dark,
    face = STYLES$font_family,
    vadjust = -15
  ))

# ---- 5. Apply shape and color per group ----

for (group_name in names(node_legend_colors_plot)) {
  net <- net %>% visGroups(
    groupname = group_name,
    color = node_legend_colors_plot[[group_name]],
    shape = node_legend_shapes_plot[[group_name]]
  )
}
# ---- 6. Add legend ----

used_groups <- unique(nodes$group)

legend_df <- tibble::tibble(
  label = used_groups,
  shape = node_legend_shapes_plot[used_groups],
  color = node_legend_colors_plot[used_groups]
) %>%
  distinct(label, .keep_all = TRUE)  # remove duplicates just in case

net <- net %>% visLegend(
  addNodes = legend_df,
  ncol = 2,                         # number of columns
  position = "left",              
  main = "Entity (Sub)Types",      # title
  useGroups = FALSE                # show custom legend entries
)
# ---- 7. Render ----
net

```

```{r}
#| echo: false
#| output: false
# ---- 1. Define styles and legends ----

event_subtypes <- c(
  "Communication", "Monitoring", "VesselMovement", "Assessment",
  "Collaborate", "Endorsement", "TourActivity", "TransponderPing",
  "Harbor Report", "Fishing", "Criticize"
)

relationship_subtypes <- c(
  "Coordinates", "AccessPermission", "Operates", "Colleagues",
  "Suspicious", "Reports", "Jurisdiction", "Unfriendly", "Friends"
)

node_legend_colors_plot <- c(
  "Person" = "#88CCEE",
  "Vessel" = "#D55E00",
  "Organization" = "#117733",
  "Location" = "#AA4499",
  "Group"= "#CC79A7",
  "Event" = "#DDCC77",         # type level
  "Relationship" = "#AF8DC3"   # type level
)

node_legend_shapes_plot <- c(
  "Person" = "dot",
  "Vessel" = "triangle",
  "Organization" = "square",
  "Location" = "diamond",
  "Group" = "circle plus",
  "Event" = "star",              # type level
  "Relationship" = "square x"    # type level
)

STYLES <- list(
  node_label_dark = "black",
  font_family = "Roboto Condensed"
)

# ---- 2. Prepare nodes ----
nodes <- mc3_nodes_final %>%
  mutate(
    label = ifelse(is.na(name), id, name),
    
    # These parts are for pulling the related data from other fields
    tooltip_extra = case_when(
      type == "Event" & sub_type == "Communication" ~ content,
      type == "Event" & sub_type == "Monitoring" ~ findings,
      type == "Event" & sub_type == "VesselMovement" ~ destination,
      type == "Event" & sub_type == "Assessment" ~ results,
      type == "Relationship" & sub_type == "Coordinates" ~ coordination_type,
      type == "Relationship" & sub_type == "Operates" ~ operational_role,
      type == "Relationship" & sub_type == "Jurisdiction" ~ jurisdiction_type,
      TRUE ~ NA_character_
    ),
    
    title = paste0(
      "<b>", label, "</b><br>",
      "Type: ", type, "<br>",
      "Sub-type: ", sub_type, "<br>",
      ifelse(!is.na(tooltip_extra), paste0("<br><b>Details:</b> ", tooltip_extra), "")
    ),
    
    # Fallback logic: if sub_type is NA or not in styling list, use type instead
    group = ifelse(sub_type %in% names(node_legend_colors_plot), sub_type, type)
  ) %>%
  select(id, label, group, title) %>%
  distinct()

# ---- 3. Prepare directed edges (type == "sent") ----

edges <- mc3_edges_final %>%
  filter(from_id %in% nodes$id & to_id %in% nodes$id) %>%
  select(from = from_id, to = to_id)

# ---- 4. Build visNetwork ----

net <- visNetwork(nodes, edges, width = "100%", height = "600px") %>%
  visEdges(arrows = list(to = list(enabled = TRUE, scaleFactor = 1.5))) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visNodes(font = list(
    size = 14,
    color = STYLES$node_label_dark,
    face = STYLES$font_family,
    vadjust = -15
  ))

# ---- 5. Apply shape and color per group ----

for (group_name in names(node_legend_colors_plot)) {
  net <- net %>% visGroups(
    groupname = group_name,
    color = node_legend_colors_plot[[group_name]],
    shape = node_legend_shapes_plot[[group_name]]
  )
}
# ---- 6. Add legend ----

used_groups <- unique(nodes$group)

legend_df <- tibble::tibble(
  label = used_groups,
  shape = node_legend_shapes_plot[used_groups],
  color = node_legend_colors_plot[used_groups]
) %>%
  distinct(label, .keep_all = TRUE)  # remove duplicates just in case

net <- net %>% visLegend(
  addNodes = legend_df,
  ncol = 2,                         # number of columns
  position = "left",              
  main = "Entity (Sub)Types",      # title
  useGroups = FALSE                # show custom legend entries
)
# ---- 7. Render ----
net

```

```{r}
#| echo: false
#| output: false
mc3_nodes_cleaned %>%
  group_by(type, sub_type) %>%
  summarize(count = n()) %>%
  arrange(-count) %>%
  kable()
```

```{r}
#| echo: false
#| output: false
# Split the 'from_id' column
mc3_edges_cleaned <- mc3_edges_cleaned %>%
  separate(from_id, into = c("from_id_supertype", "from_id_sub_type", "from_id_id"), sep = "_", remove = FALSE, extra = "drop")

# Split the 'target' column into 
mc3_edges_cleaned <- mc3_edges_cleaned %>%
  separate(to_id, into = c("to_id_supertype", "to_id_sub_type","to_id_id"), sep = "_", remove = FALSE, extra = "drop")

# Find the number of unique types in each column
unique_counts <- mc3_edges_cleaned %>%
  summarise_all(n_distinct) %>%
  pivot_longer(cols = everything(), names_to = "column", values_to = "unique_count")

# Print the unique counts for each column
print(unique_counts)
```

```{r}
#| echo: false
#| output: false
# Check the mapping
mc3_edges_cleaned %>%
  group_by(from_id_supertype, from_id_sub_type) %>%
  summarize(count = n()) %>%
  arrange(-count) %>%
  kable()

# Check the mapping
mc3_edges_cleaned %>%
  group_by(to_id_supertype, to_id_sub_type) %>%
  summarize(count = n()) %>%
  arrange(-count) %>%
  kable()
```

```{r}
#| echo: false
#| output: false
# checking for duplicates
duplicate_values1 <- mc3_nodes_cleaned %>%
  count(content) %>%
  filter(n > 1)

# View duplicates
print(duplicate_values1)
```

```{r}
#| echo: false
#| output: false
# --- 1. Extract All Communications ---
# Logic: Sender (source) --sent--> Event_Communication (target) --received--> Recipient (target)
# This extracts all communication events

# --- 2. Clean and Prepare Nodes ---
mc3_nodes_cleaned <- mc3_nodes_raw %>%
  mutate(id = as.character(id)) %>%
  filter(!is.na(id)) %>%
  distinct(id, .keep_all = TRUE) %>%
  # Rename 'type' to 'supertype' to reduce confusion with communication type
  rename(supertype = type) %>%
  # Select only columns that are needed and are consistently present
  select(id, name, sub_type, content, timestamp) 

# --- 3. Clean and Prepare Edges ---
# Rename 'type' in edges to 'edge_type' to avoid conflict with node 'supertype'
mc3_edges_cleaned <- mc3_edges_raw %>%
  rename(from_id = source,
         to_id = target,
         edge_type = type) %>% # Renamed 'type' to 'edge_type'
  mutate(across(c(from_id, to_id), as.character)) %>%
  # Filter out any edges where from_id or to_id are not in cleaned nodes
  filter(from_id %in% mc3_nodes_cleaned$id,
         to_id %in% mc3_nodes_cleaned$id)

other_communications_df <- mc3_edges_cleaned %>%
  filter(edge_type == "sent") %>% # Start with 'sent' edges
  # Join with nodes to get content and timestamp of the Event_Communication node
  left_join(mc3_nodes_cleaned %>% select(id, content, timestamp),
            by = c("to_id" = "id")) %>%
  rename(event_id = to_id, event_content = content, event_timestamp = timestamp) %>%
  # Now, find the recipient of this communication event
  left_join(mc3_edges_cleaned %>%
              filter(edge_type == "received") %>%
              select(event_id_match = from_id, recipient_id = to_id),
            by = c("event_id" = "event_id_match")) %>%
  # Join with nodes to get the sender's name and sub_type
  left_join(mc3_nodes_cleaned %>% select(id, name, sub_type),
            by = c("from_id" = "id")) %>%
  rename(sender_id_actual = from_id, sender_name = name, sender_sub_type = sub_type) %>%
  # Join with nodes to get the recipient's name and sub_type
  left_join(mc3_nodes_cleaned %>% select(id, name, sub_type),
            by = c("recipient_id" = "id")) %>%
  rename(recipient_name = name, recipient_sub_type = sub_type) %>%
  # Select and rename final columns for all communications
  select(
    communication_type = edge_type, # This will be "sent" from original filter
    sender_id = sender_id_actual,
    sender_name,
    sender_sub_type,
    recipient_id,
    recipient_name,
    recipient_sub_type,
    event_id,
    content = event_content,
    timestamp = event_timestamp
  ) 

# create a timeline visualization or inspect content.
print(knitr::kable(head(other_communications_df %>%
                          select(timestamp, sender_name, 
                                 recipient_name, content), 10),
                   format = "markdown", align = "l"))
```

```{r}
#| echo: false
#| output: false
set.seed(1234)  

# --- STEP 1: Prepare the edge list ---
edge_df <- other_communications_df %>%
  select(sender_id, recipient_id) %>%
  filter(!is.na(sender_id) & !is.na(recipient_id)) %>%
  rename(from = sender_id, to = recipient_id) %>%
  distinct()

# Remove self-loops
edge_df <- edge_df %>% filter(from != to)

# --- STEP 2: Create the graph object (undirected) ---
g <- tbl_graph(edges = edge_df, directed = FALSE)

# --- STEP 3: Run Louvain community detection ---
g <- g %>%
  mutate(community = group_louvain())

# --- STEP 4: Visualize the graph ---
ggraph(g, layout = "fr") +
  geom_edge_link(alpha = 0.3) +
  geom_node_point(aes(color = as.factor(community)), size = 5) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  theme_void() +
  labs(title = "Community Detection in Communication Network",
       color = "Community")
```

# Question 1

### 1.1 Static Chord Diagram- All Communicators

```{r, fig.width=10, fig.height=8, echo=TRUE, message=FALSE, warning=FALSE}
#| code-fold: true
#| code-summary: "Show the code"
library(tidyverse)    
library(RColorBrewer) 
library(circlize)     
library(stringr)      
# --- Step 1: Build communication matrix ---
sent_df <- other_communications_df %>%
  filter(communication_type == "sent") %>%
  count(sender_name, recipient_name, name = "sent")

received_df <- other_communications_df %>%
  filter(communication_type == "received") %>%
  count(sender_name = recipient_name, recipient_name = sender_name, name = "received")

combined_df <- full_join(sent_df, received_df, by = c("sender_name", "recipient_name")) %>%
  mutate(across(c(sent, received), ~replace_na(., 0)),
         total = sent + received)

comm_matrix <- xtabs(total ~ sender_name + recipient_name, data = combined_df)

# --- Step 2: Assign color per entity sub-type ---
type_lookup <- other_communications_df %>%
  select(name = sender_name, type = sender_sub_type) %>%
  bind_rows(other_communications_df %>% select(name = recipient_name, type = recipient_sub_type)) %>%
  distinct(name, .keep_all = TRUE)

# Define pastel Set2 colors for each type
type_colors_palette <- brewer.pal(n = 4, name = "Set2")
names(type_colors_palette) <- c("Person", "Organization", "Vessel", "Location")

# Map to nodes in the matrix
grid_colors <- type_colors_palette[type_lookup$type]
names(grid_colors) <- type_lookup$name
grid_colors <- grid_colors[rownames(comm_matrix)]

# --- Step 3: Plot chord diagram ---
circos.clear()
par(mar = c(4, 2, 8, 10))  # bottom, left, top, right

chordDiagram(
  comm_matrix,
  grid.col = grid_colors,
  transparency = 0.25,
  annotationTrack = "grid",
  preAllocateTracks = list(track.height = 0.1)
)

# Add readable sector names
circos.trackPlotRegion(
  track.index = 1,
  panel.fun = function(x, y) {
    name <- get.cell.meta.data("sector.index")
    circos.text(
      x = mean(get.cell.meta.data("xlim")),
      y = 0,
      labels = str_wrap(name, 10),
      facing = "clockwise",
      niceFacing = TRUE,
      adj = c(0, 0.5),
      cex = 0.6
    )
  },
  bg.border = NA
)

# --- Step 4: Title, subtitle ---
title(
  main = "Chord Diagram of Communication Flows",
  cex.main = 1.6,
  font.main = 2,
  line = 5
)
mtext("Each ribbon shows volume of sent + received messages", side = 3, line = 3, cex = 1, col = "gray30")
mtext("Note. Group subtype is excluded from this diagram", side = 1, line = 3, cex = 0.8, col = "gray40")

# --- Step 5: Custom Legend ---
legend_items <- names(type_colors_palette)
legend(
  x = 1.1, y = 0.85, legend = legend_items,
  fill = type_colors_palette,
  border = "gray30",
  bty = "n",
  cex = 0.7,
  pt.cex = 0.7,
  title = "Entity Sub-Type" 

)

```

::: {.callout-note title="Findings"}
The thickness of each ribbon (chord) represents the magnitude of the relationship. A thicker ribbon represents more frequent communications (sent + received) between a sender and recipient.

Here, we have an overview of paired communicators who have higher frequencies. We also can see the links between communicators. These are the entities who communicated frequently with others that we might want to focus on:

-   Person: The Intern, The Lookout, Clepper Jensen, Davis, Miranda Jordan, Mrs. Money.

-   Organization: Oceanus City Council, Green Guardian

-   Vessel: Reef Guardian, Neptune, Mako, Remora

-   Location: Himark Habor

-   Group: N/A
:::

### 1.2 Interactive Chord Diagram by Community

Here, the interactive chord diagram showed the correspondences among communities at every two hour intervals.

```{r}
#| echo: false
# Get community membership from graph object
community_df <- g %>%
  as_tibble() %>%
  select(name, community)
```

```{r, echo=TRUE, message=FALSE, warning=FALSE}
#| code-fold: true
#| code-summary: "Show the code"
library(circlize)
library(dplyr)
library(tidyr)
library(RColorBrewer)
library(stringr)
library(lubridate)
library(htmltools) # Essential for building the HTML structure
library(jsonlite) # For passing R data to JavaScript safely

# --- 1. Data Preprocessing and Setup ---

# Bin by 2-hour interval
other_communications_df <- other_communications_df %>%
  mutate(timestamp = as.POSIXct(timestamp)) %>% # Ensure timestamp is POSIXct
  mutate(timestamp_2hr = floor_date(timestamp, unit = "2 hours"))

# Get all unique 2-hour time bins for the slider
all_times <- sort(unique(other_communications_df$timestamp_2hr))

# Define output directory for image frames
output_dir <- "chord_frames"
dir.create(output_dir, showWarnings = FALSE) # Create the directory if it doesn't exist

# Community name mapping (ensure this matches  'community_df' structure)
community_name_map <- c(
  "1" = "Conservationist Group",
  "2" = "Sailor Shift",
  "3" = "Maritime",
  "4" = "Suspicious Characters",
  "5" = "Sam & Kelly",
  "6" = "Hacklee Herald"
)


# Assuming community_df has a 'community' column that's numeric/factor
if (exists("community_df") && "community" %in% names(community_df)) {
  num_unique_communities <- length(unique(community_df$community))
  base_colors <- brewer.pal(max(3, num_unique_communities), "Set2") # Use Set2 for pastel
  community_colors <- setNames(
    base_colors[1:num_unique_communities], # Slice to exactly the number needed
    as.character(sort(unique(community_df$community)))
  )
} else {
  # Fallback if community_df is not defined or missing 'community' column
  message("Warning: 'community_df' or 'community' column not found. Using default colors.")
  community_colors <- c(
    "1" = "#66C2A5", "2" = "#FC8D62", "3" = "#8DA0CB", "4" = "#E78AC3",
    "5" = "#A6D854", "6" = "#FFD92F", "7" = "#E5C494", "8" = "#B3B3B3"
  )
}


# --- 2. Generate and Save Chord Diagrams as PNGs ---

# Loop through each time bin, create a plot, and save it
for (i in seq_along(all_times)) {
  selected_time <- all_times[i]
  end_time <- selected_time + hours(2)

  filtered_df <- other_communications_df %>%
    filter(timestamp_2hr == selected_time)

  # Prepare data for the chord diagram matrix
  sent_df <- filtered_df %>%
    filter(communication_type == "sent") %>%
    count(sender_name, recipient_name, name = "sent")

  received_df <- filtered_df %>%
    filter(communication_type == "received") %>%
    count(sender_name = recipient_name, recipient_name = sender_name, name = "received")

  combined_df <- full_join(sent_df, received_df, by = c("sender_name", "recipient_name")) %>%
    mutate(across(c(sent, received), ~replace_na(., 0)),
           total = sent + received)

  # Skip this iteration if no data for the current time slice
  if (nrow(combined_df) == 0 || sum(combined_df$total) == 0) {
    message(paste("No communications for time:", selected_time, ". Skipping frame."))

    next
  }

  comm_matrix <- xtabs(total ~ sender_name + recipient_name, data = combined_df)

  # Ensure sector_names from comm_matrix exist in community_df for color mapping
  sector_names <- union(rownames(comm_matrix), colnames(comm_matrix))
  
  # Filter community_df to only relevant sectors and ensure distinct entries
  sector_community_df <- community_df %>%
    filter(name %in% sector_names) %>%
    distinct(name, .keep_all = TRUE) %>%
    arrange(match(name, sector_names))

  # Map community colors to sector names based on 'community' column
  grid_colors_current_frame <- setNames(
    community_colors[as.character(sector_community_df$community)],
    sector_community_df$name
  )
  # Ensure only colors for actual sectors in the matrix are used
  grid_colors_current_frame <- grid_colors_current_frame[names(grid_colors_current_frame) %in% sector_names]


  # Open PNG device for saving the plot
  png(sprintf("%s/frame_%03d.png", output_dir, i), width = 800, height = 800)
  
  # Clear existing circlize plot before drawing new one
  circos.clear()
  par(mar = c(6, 2, 10, 6)) # Adjust margins as needed for title and labels

  # Draw the chord diagram
  chordDiagram(
    comm_matrix,
    grid.col = grid_colors_current_frame,
    transparency = 0.25,
    annotationTrack = "grid",
    preAllocateTracks = list(track.height = 0.1)
  )

  # Add labels to the sectors
  circos.trackPlotRegion(
    track.index = 1,
    panel.fun = function(x, y) {
      name <- get.cell.meta.data("sector.index")
      wrapped_name <- str_wrap(name, width = 12)
      circos.text(
        x = mean(get.cell.meta.data("xlim")),
        y = 0,
        labels = wrapped_name,
        facing = "clockwise",
        niceFacing = TRUE,
        adj = c(0, 0.5),
        cex = 0.8
      )
    },
    bg.border = NA
  )

  # Add a main title to the plot
  title(
    main = paste("Communication Flows\n", format(selected_time, "%d %b %Y (%H:%M"), "to", format(end_time, "%H:%M)")),
    cex.main = 1.2,
    font.main = 1,
    line = 6
  )
  dev.off() # CRITICAL: Close the PNG device to save the file
}

# --- 3. Build the HTML Viewer with Embedded Images and JavaScript ---

# Generate HTML <img> tags for each saved frame
# Filter out any frames that might have been skipped if 'next' was used
# Check which frame files actually exist
existing_frames <- list.files(output_dir, pattern = "^frame_\\d{3}\\.png$", full.names = TRUE)
# Extract the numeric index from the filename to match with all_times
frame_indices <- as.numeric(gsub("frame_(\\d{3})\\.png", "\\1", basename(existing_frames)))

# Only create image tags for the frames that were successfully generated
image_tags <- lapply(seq_along(existing_frames), function(idx) {
  # The original 'i' (loop index) corresponds to the 'frame_indices'
  original_time_idx <- frame_indices[idx]
  tags$img(src = existing_frames[idx], # Use the full path here
           style = if (idx == 1) "display:block;" else "display:none;", # Show first frame by default
           class = "chord-frame",
           alt = paste("Chord diagram for time slice", format(all_times[original_time_idx], "%d %b %Y %H:%M")))
})


# JavaScript function to update which image frame is visible
# We need to map the slider value (0 to num_frames-1) to the correct time index
# because some frames might be skipped, causing gaps in numerical sequence.
js_script <- HTML(sprintf("
<script>
  // Ensure the allTimes array correctly maps to the generated frames
  const originalAllTimes = %s; // This is the full list of all_times
  const generatedFrameIndices = %s; // This indicates which original_time_idx corresponds to a generated frame

  function updateFrame(sliderIndex) {
    const frames = document.querySelectorAll('.chord-frame');
    frames.forEach((el, i) => {
      // frames[i] corresponds to existing_frames[i] from R
      // sliderIndex is 0-based for the slider
      el.style.display = (i === sliderIndex) ? 'block' : 'none';
    });

    // Update the time display text based on the current frame's original time
    const timeDisplay = document.getElementById('current-time-display');
    if (timeDisplay && sliderIndex < generatedFrameIndices.length) {
        // Get the original time index for the currently displayed frame
        const actualTimeIndex = generatedFrameIndices[sliderIndex] - 1; // Convert 1-based to 0-based for originalAllTimes
        
        if (actualTimeIndex >= 0 && actualTimeIndex < originalAllTimes.length) {
            const selectedTime = new Date(originalAllTimes[actualTimeIndex]);
            const endTime = new Date(selectedTime.getTime() + 2 * 60 * 60 * 1000); // Add 2 hours in milliseconds

            // Format dates and times for display
            const formatDate = (date) => date.toLocaleDateString('en-US', { day: '2-digit', month: 'short', year: 'numeric' });
            const formatTime = (date) => date.toLocaleTimeString('en-US', { hour: '2-digit', minute: '2-digit', hour12: false });
            
            timeDisplay.innerHTML = `Day: ${formatDate(selectedTime)} | Time: ${formatTime(selectedTime)} to ${formatTime(endTime)}`;
        } else {
            timeDisplay.innerHTML = 'No data for this time slice.';
        }
    }
  }

  // Initialize the display on page load
  document.addEventListener('DOMContentLoaded', () => {
    const slider = document.getElementById('frameSlider');
    if (slider) {
        updateFrame(parseInt(slider.value)); // Set initial frame based on slider's default value
    }
  });
</script>
", jsonlite::toJSON(as.character(all_times)), jsonlite::toJSON(frame_indices))) # Pass all_times and frame_indices to JS


# --- 4. Display the HTML content directly in the Quarto document ---
# This is the key line to make Quarto embed the interactive viewer.
browsable(
  tagList(
    js_script, # The JavaScript for interactivity
    tags$head(
      tags$style(HTML("
        /* Basic styling for the image frames and slider container */
        .chord-frame { width: 100%; max-width: 800px; height: auto; margin: auto; display: block; }
        #slider-container { text-align: center; margin: 20px auto; max-width: 800px; }
        .chord-title { text-align: center; font-size: 1.5em; margin-bottom: 15px; font-weight: bold; }
        #frameSlider { width: 80%; max-width: 700px; margin: 10px auto; display: block; }
        #current-time-display { font-weight: bold; margin-top: 10px; }
      "))
    ), # Close tags$head

    tags$body( 
      tags$div(class = "chord-title", "Interactive Communication Flows Over Time"),
      tags$div(id = "slider-container",
          tags$input(type = "range", min = "0", max = length(existing_frames) - 1, value = 0,
                     id = "frameSlider", oninput = "updateFrame(parseInt(this.value))"),
          tags$p(id = "current-time-display", style = "font-weight:bold; margin-top: 10px;"),
          tags$p("Use the slider to view communication over time")
      ),
      tags$div(id = "chord-images-container", image_tags) # Container for all image frames
    )
  )
)
```

::: {.callout-note title="1.2 Findings"}
We noticed some cross community direct and indirect communication occured mainly among influential nodes, suggesting collaboration. These are **some** sample linkages with arrows regardless of sent or received:

+-----------------------+-------------------------------------------------------------+
| Community X           | Node Linkages (Community X -\> Community X -\> Community Y) |
+=======================+=============================================================+
| Suspicious Characters | Mrs. Money -\> Intern -\> The Lookout                       |
|                       |                                                             |
|                       | Liam -\> Paackland Harbor -\> The Middleman                 |
|                       |                                                             |
|                       | Glitters Team -\> Boss -\> Mako                             |
|                       |                                                             |
|                       | Glitters Team -\> Samantha Blake -\> Sailor Shifts Team     |
+-----------------------+-------------------------------------------------------------+
| Sailor Shift          | Neptune -\> Elise -\> Mako                                  |
|                       |                                                             |
|                       | Neptune -\> Davis -\> Mako                                  |
|                       |                                                             |
|                       | Remora -\> Neptune -\> Boss                                 |
|                       |                                                             |
|                       | Rodriguez -\> Remora -\> Mako                               |
|                       |                                                             |
|                       | Remora -\> Small Fry -\> Mako                               |
|                       |                                                             |
|                       | Davis -\> Remora -\> Paackland Harbor                       |
|                       |                                                             |
|                       | V. Miesel Shipping -\> Neptune -\> Mako                     |
+-----------------------+-------------------------------------------------------------+
| Sam & Kelly           | Kelly -\> Sam - \> The Lookout                              |
+-----------------------+-------------------------------------------------------------+
| Maritime              | Mako -\> Himark Harbor -\> Oceanus City Council             |
+-----------------------+-------------------------------------------------------------+
| Hacklee Herald        | N/A (Only Direct Community X to X communications)           |
+-----------------------+-------------------------------------------------------------+
| Conservationist Group | Reef Guardian -\> Oceanus City Council -\> Nadia            |
|                       |                                                             |
|                       | Reef Guardian -\> Paackland Harbor -\> Mako                 |
|                       |                                                             |
|                       | Oceanus City Council -\> Liam -\> Nadia                     |
+-----------------------+-------------------------------------------------------------+
:::

We also noticed that at times, certain individuals sent messages but there were no response back. This could possibly be due to the pseudonyms being used to send or reply to the same content. For instance, there was a message from Davis to Rodriguez on 14 Oct around 1200-1400 but there was no response by Rodriguez. By looking at the content field, we then found out that he was Small Fry due to the responses he provided to Davis which was originally addressed to Rodriguez.

### 1.3 Heatmap of Correspondences

::: panel-tabset
## Heatmap of Correspondences

```{r}
#| echo: false
# Step 1: Count interactions
adj_df <- other_communications_df %>%
  count(sender_name, recipient_name, name = "count")

# Step 2: Compute total sent and received counts
sender_order <- adj_df %>%
  group_by(sender_name) %>%
  summarise(total_sent = sum(count)) %>%
  arrange(desc(total_sent)) %>%
  pull(sender_name)

recipient_order <- adj_df %>%
  group_by(recipient_name) %>%
  summarise(total_received = sum(count)) %>%
  arrange(desc(total_received)) %>%
  pull(recipient_name)

# Step 3: Reorder factor levels
adj_df <- adj_df %>%
  mutate(
    sender_name = factor(sender_name, levels = sender_order),
    recipient_name = factor(recipient_name, levels = recipient_order)
  )

# Step 4: Plot heatmap
ggplot(adj_df, aes(x = recipient_name, y = sender_name, fill = count)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "navyblue") +
  labs(
    title = "Sender-Recipient Communication Heatmap",
    subtitle = "Top communicators sorted to bottom-left",
    x = "Recipient",
    y = "Sender",
    fill = "Messages"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(size = 12, face = "bold"),
    plot.subtitle = element_text(size = 10),
    panel.grid = element_blank()
  )
```

## The Code

```{r}
#| echo: true
#| eval: false
# Step 1: Count interactions
adj_df <- other_communications_df %>%
  count(sender_name, recipient_name, name = "count")

# Step 2: Compute total sent and received counts
sender_order <- adj_df %>%
  group_by(sender_name) %>%
  summarise(total_sent = sum(count)) %>%
  arrange(desc(total_sent)) %>%
  pull(sender_name)

recipient_order <- adj_df %>%
  group_by(recipient_name) %>%
  summarise(total_received = sum(count)) %>%
  arrange(desc(total_received)) %>%
  pull(recipient_name)

# Step 3: Reorder factor levels
adj_df <- adj_df %>%
  mutate(
    sender_name = factor(sender_name, levels = sender_order),
    recipient_name = factor(recipient_name, levels = recipient_order)
  )

# Step 4: Plot heatmap
ggplot(adj_df, aes(x = recipient_name, y = sender_name, fill = count)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "navyblue") +
  labs(
    title = "Sender-Recipient Communication Heatmap",
    subtitle = "Top communicators sorted to bottom-left",
    x = "Recipient",
    y = "Sender",
    fill = "Messages"
  ) +
  theme_minimal(base_size = 10) +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    plot.title = element_text(size = 12, face = "bold"),
    plot.subtitle = element_text(size = 10),
    panel.grid = element_blank()
  )
```
:::

::: {.callout-note title="1.3 Findings"}
After extraction of the entities who communicated frequently (from the Static Chord Diagram), we tabled who they communicated with by using the heatmap. E.g. Name1 communicated with Name2.

+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Name 1 Subtype | Name1                | Name2                                                                                                                                                     |
+================+======================+===========================================================================================================================================================+
| Person         | The Intern           | The Lookout, Mrs. Money                                                                                                                                   |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Person         | Clepper Jensen       | Miranda Jordan                                                                                                                                            |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Person         | Davis                | Neptune                                                                                                                                                   |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Person         | Mrs. Money           | The Intern, The Middleman, Boss                                                                                                                           |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Vessel         | Mako                 | Remora, Green Guardians, Oceanus City Council, Neptune, Reef Guardians, Himark Harbor, Davis, Sentinel, Paackland Habor, Samantha Blake, Serenity, Osprey |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Vessel         | Remora               | Mako, Neptune, Himark Habor, Davis, Paackland Harbor, V. Miesel Shipping, Marlin, Small Fry                                                               |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Vessel         | Neptune              | Mako, Himark Habor, Remora, Mrs Money, V. Miesel Shipping, Nadia, Serenity                                                                                |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Vessel         | Reef Guardian        | Green Guardians, Oceanus City Council, Mako, Paackland Harbor, EcoVigil, Serenity, Defender                                                               |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Organization   | Green Guardian       | Green Guardians, Oceanus City Council, The Lookout, Sentinel, Horizon                                                                                     |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Organization   | Oceanus City Council | Green Guardians, Reef Guardians, Himark Harbor, Sentinel, Paackland Harbor, Liam Thorne, Samantha Blake, Haacklee Harbor                                  |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
| Location       | Himark Habor         | Oceanus City Council, Mako, Serenity, Marlin                                                                                                              |
+----------------+----------------------+-----------------------------------------------------------------------------------------------------------------------------------------------------------+
:::

### 1.4 Heatmap of date and hours

::: panel-tabset
## Heatmap of date and hours

```{r, message=FALSE, warning=FALSE}
#| echo: false
# Load data
MC3_graph <- fromJSON("data/MC3_graph.json")
nodes_tbl  <- as_tibble(MC3_graph$nodes)
edges_tbl  <- as_tibble(MC3_graph$edges)

# Extract only the communication events
comm_nodes <- nodes_tbl %>%
  filter(type == "Event", sub_type == "Communication") %>%
  select(event_id = id, timestamp)

# Pull out who sent and who received each message
sent_edges <- edges_tbl %>%
  filter(type == "sent") %>%
  select(sender = source, event_id = target)

recv_edges <- edges_tbl %>%
  filter(type == "received") %>%
  select(event_id = source, receiver = target)

#  Join everything together and parse the timestamp
msgs <- sent_edges %>%
  inner_join(recv_edges, by = "event_id") %>%
  inner_join(comm_nodes, by = "event_id") %>%
  mutate(
    ts   = ymd_hms(timestamp, tz = "UTC"),
    date = as_date(ts),
    hour = hour(ts)
  )

# Build a complete date×hour grid, filling in zeros where needed
heatmap_data <- msgs %>%
  count(date, hour) %>%
  complete(
    date = seq(min(date), max(date), by = "1 day"),
    hour = 0:23,
    fill = list(n = 0)
  )

#Plot the heatmap
ggplot(heatmap_data, aes(x = hour, y = date, fill = n)) +
  geom_tile(color = "white") +
  scale_x_continuous(
    breaks = 0:23,
    expand = c(0, 0)
  ) +
  scale_y_date(
    breaks      = seq(min(heatmap_data$date), max(heatmap_data$date), by = "1 day"),
    date_labels = "%b %d",
    expand      = c(0, 0)
  ) +
  scale_fill_distiller(
    name    = "Messages",
    palette = "Spectral",
    direction = 1
  ) +
  labs(
    title = "Daily Communication Patterns",
    x     = "Hour of Day",
    y     = "Date"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(hjust = 0.5),
    axis.text.y = element_text(size = 8),
    panel.grid  = element_blank()
  )

```

## The code

```{r, message=FALSE, warning=FALSE}
#| echo: true
#| eval: false

# Load data
MC3_graph <- fromJSON("data/MC3_graph.json")
nodes_tbl  <- as_tibble(MC3_graph$nodes)
edges_tbl  <- as_tibble(MC3_graph$edges)

# Extract only the communication events
comm_nodes <- nodes_tbl %>%
  filter(type == "Event", sub_type == "Communication") %>%
  select(event_id = id, timestamp)

# Pull out who sent and who received each message
sent_edges <- edges_tbl %>%
  filter(type == "sent") %>%
  select(sender = source, event_id = target)

recv_edges <- edges_tbl %>%
  filter(type == "received") %>%
  select(event_id = source, receiver = target)

#  Join everything together and parse the timestamp
msgs <- sent_edges %>%
  inner_join(recv_edges, by = "event_id") %>%
  inner_join(comm_nodes, by = "event_id") %>%
  mutate(
    ts   = ymd_hms(timestamp, tz = "UTC"),
    date = as_date(ts),
    hour = hour(ts)
  )

# Build a complete date×hour grid, filling in zeros where needed
heatmap_data <- msgs %>%
  count(date, hour) %>%
  complete(
    date = seq(min(date), max(date), by = "1 day"),
    hour = 0:23,
    fill = list(n = 0)
  )

#Plot the heatmap
ggplot(heatmap_data, aes(x = hour, y = date, fill = n)) +
  geom_tile(color = "white") +
  scale_x_continuous(
    breaks = 0:23,
    expand = c(0, 0)
  ) +
  scale_y_date(
    breaks      = seq(min(heatmap_data$date), max(heatmap_data$date), by = "1 day"),
    date_labels = "%b %d",
    expand      = c(0, 0)
  ) +
  scale_fill_distiller(
    name    = "Messages",
    palette = "Spectral",
    direction = 1
  ) +
  labs(
    title = "Daily Communication Patterns",
    x     = "Hour of Day",
    y     = "Date"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(hjust = 0.5),
    axis.text.y = element_text(size = 8),
    panel.grid  = element_blank()
  )


```
:::

### 1.5 Hourly Communication Patterns: Week 1 vs Week 2

::: panel-tabset
## Compare the communication pattern

```{r}
#| echo: false

msgs <- msgs %>%
  mutate(
    week = if_else(date <= min(date) + days(6), "Week 1", "Week 2")
  )
# Count and normalize within each week
week_patterns <- msgs %>%
  count(week, hour) %>%
  group_by(week) %>%
  mutate(proportion = n / sum(n))


hour_breaks <- seq(min(week_patterns$hour), max(week_patterns$hour), by = 1)
prop_breaks <- seq(
  0,
  ceiling(max(week_patterns$proportion) * 100) / 100,
  by = 0.02
)

ggplot(week_patterns, aes(x = hour, y = proportion, color = week)) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  scale_x_continuous(breaks = hour_breaks) +
  scale_y_continuous(
    breaks = prop_breaks,
    labels = percent_format(accuracy = 1)
  ) +
  labs(
    title = "Hourly Communication Patterns: Week 1 vs Week 2",
    x     = "Hour of Day",
    y     = "Percent of Total Messages"
  ) +
  theme_light(base_size = 12) +
  theme(
    plot.title      = element_text(face = "bold", size = 16, hjust = 0.5),
    legend.position = "top",
    legend.title    = element_blank(),
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_line(color = "grey90"),
    axis.text.x     = element_text(vjust = 0.5),
    axis.text.y     = element_text(size = 8)
  )


```

## The code

```{r}
#| echo: true 
#| eval: false
msgs <- msgs %>%
  mutate(
    week = if_else(date <= min(date) + days(6), "Week 1", "Week 2")
  )
# Count and normalize within each week
week_patterns <- msgs %>%
  count(week, hour) %>%
  group_by(week) %>%
  mutate(proportion = n / sum(n))


hour_breaks <- seq(min(week_patterns$hour), max(week_patterns$hour), by = 1)
prop_breaks <- seq(
  0,
  ceiling(max(week_patterns$proportion) * 100) / 100,
  by = 0.02
)

ggplot(week_patterns, aes(x = hour, y = proportion, color = week)) +
  geom_line(size = 1.2) +
  geom_point(size = 3) +
  scale_x_continuous(breaks = hour_breaks) +
  scale_y_continuous(
    breaks = prop_breaks,
    labels = percent_format(accuracy = 1)
  ) +
  labs(
    title = "Hourly Communication Patterns: Week 1 vs Week 2",
    x     = "Hour of Day",
    y     = "Percent of Total Messages"
  ) +
  theme_light(base_size = 12) +
  theme(
    plot.title      = element_text(face = "bold", size = 16, hjust = 0.5),
    legend.position = "top",
    legend.title    = element_blank(),
    panel.grid.major = element_line(color = "grey80"),
    panel.grid.minor = element_line(color = "grey90"),
    axis.text.x     = element_text(vjust = 0.5),
    axis.text.y     = element_text(size = 8)
  )

```
:::

::: {.callout-note title="Findings"}
The visualization of hourly communication patterns reveals that message activity in Oceanus follows a pronounced daily cycle, with distinct peaks and lows across both observed weeks.

In Week 1, communication is highly concentrated in the morning hours, particularly between 8 AM and 12 PM, where a majority of the messages are exchanged.

By contrast, Week 2 shows a broader distribution of communication throughout the day, with notable increases in afternoon and evening activity.

This shift suggests that while the first week’s communications were more focused and possibly related to regular planning or operational updates, the second week’s patterns reflect heightened activity or more dynamic coordination, potentially due to emergent events or increased urgency among entities.
:::

# Question 2

### Question 2a)

### 2.1 Unique count from each sender subtype

::: panel-tabset
## Unique Count

```{r, echo=FALSE}
sender_names_by_type <- other_communications_df %>%
  group_by(sender_sub_type) %>%
  summarise(
    unique_senders = n_distinct(sender_name),
    sender_names = paste(sort(unique(sender_name)), collapse = ", ")
  ) %>%
  arrange(desc(unique_senders))  # sort from largest to smallest

# View the table
print(sender_names_by_type)
```

## The Code

```{r}
#| echo: true
#| eval: false
sender_names_by_type <- other_communications_df %>%
  group_by(sender_sub_type) %>%
  summarise(
    unique_senders = n_distinct(sender_name),
    sender_names = paste(sort(unique(sender_name)), collapse = ", ")
  ) %>%
  arrange(desc(unique_senders))  # sort from largest to smallest

# View the table
print(sender_names_by_type)
```

::: callout-note
There were no Group sub-type as confirmed by this filtered table.
:::
:::

## 2.2 People and Vessels

### 2.2.1 Filter by Vessel and Person only

```{r}
person_vessel_df <- other_communications_df %>%
  filter(
    (sender_sub_type == "Person" & recipient_sub_type == "Vessel") |
    (sender_sub_type == "Vessel" & recipient_sub_type == "Person") |
    (sender_sub_type == "Person" & recipient_sub_type == "Person") |
    (sender_sub_type == "Vessel" & recipient_sub_type == "Vessel")
  )
```

### 2.2.2 Plotted Timeline- People & Vessels

```{r}
#| code-fold: true
#| code-summary: "Show the code"
# --- FACTORING and DATETIME CLEANING ---
person_vessel_df_for_plot <- person_vessel_df %>%
  mutate(
    timestamp = as.POSIXct(timestamp),
    comm_date = as.Date(timestamp),
    comm_time_of_day = hms::as_hms(format(timestamp, "%H:%M:%S")),
    sender_sub_type = factor(sender_sub_type, levels = c("Person", "Vessel")),
    communicating_pair_sorted = paste(pmin(sender_name, recipient_name), pmax(sender_name, recipient_name), sep = " & ")
  )

# --- WRAPPING CONTENT AND TOOLTIP ---
plot_data1 <- person_vessel_df_for_plot %>%
  mutate(
    timestamp = as.POSIXct(timestamp),
    date = as.Date(timestamp),
    time = format(timestamp, "%H:%M:%S"),
    wrapped_content = str_wrap(content, width = 50),
    tooltip_text = paste0(
      "<b>Date:</b> ", date, "<br>",
      "<b>Time:</b> ", time, "<br>",
      "<b>From:</b> ", sender_name, "<br>",
      "<b>To:</b> ", recipient_name, "<br>",
      "<b>Event_id:</b> ", event_id, "<br><br>",
      "<b>Content:</b><br>", wrapped_content
    )
  )

# Plot
p <-ggplot(plot_data1, aes(x = comm_date, y = comm_time_of_day)) +
  geom_point(aes(
    color = sender_id,
    shape = sender_sub_type,
    text = tooltip_text
  ),show.legend = c(color = TRUE, shape = FALSE), 
  size = 2, alpha = 0.7) +
  scale_shape_manual(values = c("Person" = 16, "Vessel" = 17)) +
  facet_wrap(~ sender_sub_type, ncol = 1, scales = "fixed") +
  scale_y_time(
    limits = hms::as_hms(c("08:00:00", "14:00:00")),  # reversed to show time top-to-bottom
    breaks = hms::as_hms(c("08:00:00", "09:00:00", "10:00:00", "11:00:00", "12:00:00", "13:00:00", "14:00:00")),
    labels = c("08:00", "09:00", "10:00", "11:00", "12:00", "13:00", "14:00")
)+
  scale_x_date(
  date_breaks = "1 day",
  date_labels = "%d %b"
)+
  labs(
    title = "Communication Events Over Time (Sender's Perspective)",
    x = "Date",
    y = "Time of Day",
    color = "Sender (subtype, name)"
  ) +
  theme_grey() +
  theme(
    axis.text.y = element_text(size = 6),
    axis.title.y = element_text(size = 7),
    axis.ticks.y = element_line(),
    axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 8), size = 7),
    panel.spacing = unit(0.5, "lines"),  # Applies to both x and y spacing
    strip.text = element_text(size = 8, face = "bold"),
    legend.position = "bottom",
    legend.text = element_text(size = 6),
    legend.title = element_blank()
  )

# --- Convert to interactive plot ---
ggplotly(p, tooltip = "tooltip_text")
```

#### 2.2.3 Findings on People/ Vessels:

::: {.callout-note title="Findings"}
-   Core logic:

    -   If two names appear as sender and recipient in the same message, they cannot belong to the same person — i.e., they're not aliases of each other.

    -   If two names sent a message at the exact time, they cannot belong to the same person.

    -   For instance, if Nadia sent a message to The Accountant, they would not be the same individual. If Nadia sent a message at 10am to The Accountant and The Lookout also sent a message at 10am to The Intern, Nadia and The Lookout cannot be the same person.

-   Select only The Accountant, Mrs. Money, Elise: We see close timings between Mrs. Money and Elise on 8 Oct, and 10 Oct. These were on the same topic. Elise then disappears from radar on 10 Oct. She reappears as The Accountant and Mrs. Money on 11 Oct on the same topic and remains only as The Accountant till 14 Oct.

-   Select only Liam and The Middleman: The Middleman disappeared on 7 Oct and appeared as Liam on 8 Oct. On 11 Oct Mrs. Money asked The Middleman if anything was found by conservation vessels. On the same day, Liam reappeared and replied Elise that nothing was found by them.

-   Select only The Boss and Nadia: The Boss disappeared on 5 Oct and reappeared as Nadia on 8 Oct. Likely the same person.

-   Select only Small Fry and Rodriguez: on 2 Oct Rodriguez corresponded with Remora and Mako on meeting at the slip #14. It happened again on 14 Oct as he took on dual roles and responded to the same message with different names. Likely the same person.

-   Select only The Lookout and Sam: on 7 Oct Sam asked Kelly to get information on who authorized the permit. 2 minutes later, The Lookout (Kelly) responded to The Intern (Sam), that it was signed by Jensen from City Council.

-   Seawatch only appeared on 10 Oct but Horizon talked to Seawatch on 8 Oct. Therefore, some other entity is Seawatch before or during 8 Oct. Defender told Seawatch on 3 Oct at 8.39am that it increased its patrol and informed Seawatch to maintain vigilance. The Lookout (Seawatch) responded to Sentinel (Defender) at 8.41am that it acknowledged the need for vigilance.
:::

### Question 2b)

### 2.3 Centrality Measure- People & Vessels

```{r,echo=FALSE}
set.seed(1234)

# --- STEP 1: Prepare the edge list ---
edge_df_pv <- person_vessel_df %>%
  select(sender_id, recipient_id) %>%
  filter(!is.na(sender_id) & !is.na(recipient_id)) %>%
  rename(from = sender_id, to = recipient_id) %>%
  distinct()

# Optional: remove self-loops
edge_df_pv <- edge_df_pv %>% filter(from != to)

# --- STEP 2: Create the graph object (undirected) ---
g_pv <- tbl_graph(edges = edge_df_pv, directed = FALSE)

# --- STEP 3: Run Louvain community detection ---
g_pv <- g_pv %>%
  mutate(community = group_louvain())

# --- STEP 4: Visualize the graph ---
ggraph(g_pv, layout = "fr") +
  geom_edge_link(alpha = 0.3) +
  geom_node_point(aes(color = as.factor(community)), size = 5) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  theme_void() +
  labs(title = "Community Detection in Communication Network",
       color = "Community")
```

::: panel-tabset
## PageRank Centrality Algorithm

```{r, echo=FALSE}

# --- Compute Centrality Measures ---
set.seed(1234)
g_pv <- g_pv %>%
  mutate(
    pagerank = centrality_pagerank(),
    degree = centrality_degree(),
    betweenness = centrality_betweenness(),
    closeness = centrality_closeness()
  )

# Show top 10 nodes by PageRank
g_pv %>%
  as_tibble() %>%
  select(name, pagerank, degree, betweenness, closeness) %>%
  arrange(desc(pagerank)) %>%
  head(10)
```

## The Network

```{r, echo=FALSE}
set.seed(1234)

# Visualize by Centrality
ggraph(g_pv, layout = "fr") +
  geom_edge_link(alpha = 0.3) +
  geom_node_point(aes(size = pagerank, color = as.factor(community)), alpha = 0.8) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  theme_void() +
  labs(title = "Network with PageRank Centrality",
       size = "PageRank", color = "Community")
```

## The Code

```{r}
#| echo: true 
#| eval: false
set.seed(1234)

# --- STEP: Compute Centrality Measures ---
g_pv <- g_pv %>%
  mutate(
    pagerank = centrality_pagerank(),
    degree = centrality_degree(),
    betweenness = centrality_betweenness(),
    closeness = centrality_closeness()
  )

# Show top 10 nodes by PageRank
g_pv %>%
  as_tibble() %>%
  select(name, pagerank, degree, betweenness, closeness) %>%
  arrange(desc(pagerank)) %>%
  head(10)

# Visualize by Centrality
ggraph(g_pv, layout = "fr") +
  geom_edge_link(alpha = 0.3) +
  geom_node_point(aes(size = pagerank, color = as.factor(community)), alpha = 0.8) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  theme_void() +
  labs(title = "Network with PageRank Centrality",
       size = "PageRank", color = "Community")
```
:::

::: {.callout-note title="2.3.1 Findings:"}
-   There were 5 closely associated groups. Community 5 (Clepper and Miranda) appeared to be segmented from the central group, due to the non-involvement from the nature of their investigative work.
-   From the graph, we extracted the 8 influential nodes to focus on:
    -   Community 1: Mako
    -   Community 2: Neptune, Remora, Nadia, Davis
    -   Community 3: N/A as they were not very influential at global level
    -   Community 4: Mrs. Money, Boss, The Middleman
    -   Community 5: N/A as they were not very influential at global level
:::

### 2.4 Wordclouds- Bigrams

We focused on bigrams here to get more contextual data from two instead of one word.

::: panel-tabset
## The Wordclouds

```{r}
#| echo: false
#| output: false
# 1. Extract node community assignments
g_node_communities <- g %>%
  as_tibble() %>%
  select(sender_name = name, community)

# 2. Join communication content with community assignments
content_with_community <- other_communications_df %>%
  left_join(g_node_communities, by = c("sender_name")) %>%
  filter(!is.na(community), !is.na(content))

# 3. Unnest tokens for unigrams
unigrams <- content_with_community %>%
  unnest_tokens(word, content, token = "words") %>%
  anti_join(stop_words, by = "word") %>%
  count(community, word, sort = TRUE)

# 4. Unnest tokens for bigrams
bigrams <- content_with_community %>%
  unnest_tokens(bigram, content, token = "ngrams", n = 2) %>%
  separate(bigram, into = c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% stop_words$word,
         !word2 %in% stop_words$word) %>%
  unite(bigram, word1, word2, sep = " ") %>%
  count(community, bigram, sort = TRUE)

# 5a. Plot word clouds per community
par(mfrow = c(2, 3))  # 2 rows, 3 columns layout for 6 communities
for (i in sort(unique(bigrams$community))) {
  words <- bigrams %>% filter(community == i)
  
  if (nrow(words) < 1) next  # Skip if no words
  
  suppressWarnings({
    set.seed(432)  # Set seed for reproducibility
    wordcloud(words = words$bigram,  # <-- FIXED here
              freq = words$n,
              max.words = min(20, nrow(words)),
              scale = c(3, 0.5),
              colors = brewer.pal(8, "Dark2"),
              random.order = FALSE)
  })
  mtext(paste("Community", i), side = 3, line = 1, adj = 0.5, cex = 1.5, col = "black")
}

```

```{r}
#| echo: false
# 5b. Plot word clouds per community
valid_communities <- unique(g_pv %>% as_tibble() %>% pull(community))

par(mfrow = c(2, 3))  # Still allocate 6 slots, but you can adjust this
for (i in sort(valid_communities)) {
  words <- bigrams %>% filter(community == i)
  
  if (nrow(words) < 1) next
  
  suppressWarnings({
    set.seed(432)  # Set seed for reproducibility
    wordcloud(words = words$bigram,  # <-- FIXED here
              freq = words$n,
              max.words = min(30, nrow(words)),
              scale = c(3, 0.5),
              colors = brewer.pal(8, "Dark2"),
              random.order = FALSE)
  })
  mtext(paste("Community", i), side = 3, line = 1, adj = 0.5, cex = 1.5, col = "black")
}
```

## The Code

```{r}
#| echo: true 
#| eval: false
# 5b. Plot word clouds per community
valid_communities <- unique(g_pv %>% as_tibble() %>% pull(community))

par(mfrow = c(2, 3))  # Still allocate 6 slots, but you can adjust this
for (i in sort(valid_communities)) {
  words <- bigrams %>% filter(community == i)
  
  if (nrow(words) < 1) next
  
  suppressWarnings({
    set.seed(432)  # Set seed for reproducibility
    wordcloud(words = words$bigram,  # <-- FIXED here
              freq = words$n,
              max.words = min(30, nrow(words)),
              scale = c(3, 0.5),
              colors = brewer.pal(8, "Dark2"),
              random.order = FALSE)
  })
  mtext(paste("Community", i), side = 3, line = 1, adj = 0.5, cex = 1.5, col = "black")
}
```
:::

### 2.5 Circular barchart for Top Bigrams per Community

::: panel-tabset
## The Circular Barchart

```{r, echo=FALSE, message=FALSE, warning=FALSE, `fig-width`=8, `fig-height`=8}
set.seed(1234)

valid_communities <- g_pv %>%
  as_tibble() %>%
  distinct(community) %>%
  pull(community)

bigrams <- bigrams %>% filter(community %in% valid_communities)

# --- Configuration ---
num_top_bigrams_per_community <- 8
empty_bar_count <- 2 # gaps btw comm.
#excluded_community <- 5 # too little in community 5

# --- 1. Prepare the Combined Dataset ---
all_communities_data <- bigrams %>%
#  filter(community != excluded_community) %>%
  group_by(community) %>%
  arrange(desc(n)) %>%
  slice_head(n = num_top_bigrams_per_community) %>%
  ungroup()

all_communities_data$community <- as.factor(all_communities_data$community)

to_add <- data.frame(
  bigram = NA,
  n = NA,
  community = rep(levels(all_communities_data$community), each = empty_bar_count)
)

plot_data <- rbind(all_communities_data, to_add) %>%
  arrange(community)

plot_data$id <- seq_len(nrow(plot_data)) # Keep ID as numeric here

# --- 2. Prepare Label Data ---
label_data <- plot_data
number_of_bar <- nrow(label_data)
label_data$angle <- 90 - 360 * (label_data$id - 0.5) / number_of_bar
label_data$hjust <- ifelse(label_data$angle < -90, 1, 0)
label_data$angle <- ifelse(label_data$angle < -90, label_data$angle + 180, label_data$angle)

# --- 3. Prepare Data for Baselines (Community Dividers) ---
base_data <- plot_data %>%
  group_by(community) %>%
  summarize(
    start = min(id, na.rm = TRUE), # Keep as numeric
    end = max(id, na.rm = TRUE) - empty_bar_count # Keep as numeric
  ) %>%
  rowwise() %>%
  mutate(
    title_position = mean(c(start, end))
  ) %>%
  ungroup()

# --- 4. Prepare Data for Grid Lines (Optional: Value Scales) ---
max_n_value <- max(plot_data$n, na.rm = TRUE)
grid_lines_values <- c(20, 40, 60, 80, 100)
grid_lines_values <- grid_lines_values[grid_lines_values <= max_n_value]

grid_segments_data <- plot_data %>%
  group_by(community) %>%
  summarize(
    start_id = min(id, na.rm = TRUE), # Keep as numeric
    end_id = max(id, na.rm = TRUE) - empty_bar_count # Keep as numeric
  )

grid_data_final <- tibble()
for(val in grid_lines_values) {
  temp_data <- grid_segments_data %>%
    mutate(y_value = val)
  grid_data_final <- bind_rows(grid_data_final, temp_data)
}

# --- Data for grid line LABELS ---
grid_label_data <- data.frame(
  x_pos = max(plot_data$id, na.rm = TRUE) + 2, # Fixed x position outside the plot
  y_pos = grid_lines_values,
  label_text = as.character(grid_lines_values)
)

# --- 5. Make the Unified Plot ---
p <- ggplot(plot_data, aes(x = id, y = n, fill = community)) + # <--- x = id (numeric)
  # Add background grid lines for value (e.g., 20, 40, 60, 80)
  geom_segment(data = grid_data_final,
               aes(x = start_id - 0.5, y = y_value, xend = end_id + 0.5, yend = y_value),
               inherit.aes = FALSE,
               color = "grey", alpha = 0.8, linewidth = 0.3) +

  # Add text showing the value of each grid line at a fixed position
  geom_text(data = grid_label_data,
            aes(x = x_pos, y = y_pos, label = label_text),
            inherit.aes = FALSE,
            color = "grey", size = 3, angle = 0, fontface = "bold", hjust = 0) +

  # Bars for the bigrams (main plot elements)
  geom_bar(stat = "identity", alpha = 0.8, color = "white", linewidth = 0.1,
           width = 1) + # <--- Add width=1 to remove space between bars if id is numeric

  # Set limits for the y-axis, providing space for labels
  ylim(-max_n_value * 0.7, max_n_value * 1.2) +

  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm") # Top, Right, Bottom, Left margins
  ) +
  coord_polar(start = 0) +

  # Add bigram labels
  geom_text(
    data = label_data,
    aes(x = id, y = n + 10, label = bigram, hjust = hjust), # <--- x = id (numeric)
    color = "black", fontface = "bold", alpha = 0.8, size = 2.8,
    angle = label_data$angle, inherit.aes = FALSE
  ) +

  # Add base lines for each community segment
  geom_segment(
    data = base_data,
    aes(x = start - 0.5, y = -10, xend = end + 0.5, yend = -10),
    colour = "black", alpha = 0.8, linewidth = 0.6, inherit.aes = FALSE
  ) +

  # Add community group labels
  geom_text(
    data = base_data,
    aes(x = title_position, y = -40, label = paste("Comm.", community)),
    colour = "black", alpha = 0.9, size = 2, fontface = "bold", inherit.aes = FALSE
  )+
  # --- Add the Title ---
  labs(
    title = "Circular Bar Chart by Community",
    subtitle = "Frequencies of key bigrams within each community", # Updated subtitle
    caption = paste0("AT | Generated: ", Sys.Date())
  ) +
  # Apply the Set2 Brewer palette
  scale_fill_brewer(palette = "Set2") +
  # --- Customize title appearance ---
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold", margin = margin(b = 10)),
    plot.subtitle = element_text(hjust = 0.5, size = 12, margin = margin(b = 10)),
    plot.caption = element_text(hjust = 1, size = 7, color = "grey50")
  )

print(p)
```

## The Code

```{r}
#| echo: true 
#| eval: false 
set.seed(1234)


valid_communities <- g_pv %>%
  as_tibble() %>%
  distinct(community) %>%
  pull(community)

bigrams <- bigrams %>% filter(community %in% valid_communities)

# --- Configuration ---
num_top_bigrams_per_community <- 8
empty_bar_count <- 2 # gaps btw comm.
#excluded_community <- 5 # too little in community 5

# --- 1. Prepare the Combined Dataset ---
all_communities_data <- bigrams %>%
#  filter(community != excluded_community) %>%
  group_by(community) %>%
  arrange(desc(n)) %>%
  slice_head(n = num_top_bigrams_per_community) %>%
  ungroup()

all_communities_data$community <- as.factor(all_communities_data$community)

to_add <- data.frame(
  bigram = NA,
  n = NA,
  community = rep(levels(all_communities_data$community), each = empty_bar_count)
)

plot_data <- rbind(all_communities_data, to_add) %>%
  arrange(community)

plot_data$id <- seq_len(nrow(plot_data)) # Keep ID as numeric here

# --- 2. Prepare Label Data ---
label_data <- plot_data
number_of_bar <- nrow(label_data)
label_data$angle <- 90 - 360 * (label_data$id - 0.5) / number_of_bar
label_data$hjust <- ifelse(label_data$angle < -90, 1, 0)
label_data$angle <- ifelse(label_data$angle < -90, label_data$angle + 180, label_data$angle)

# --- 3. Prepare Data for Baselines (Community Dividers) ---
base_data <- plot_data %>%
  group_by(community) %>%
  summarize(
    start = min(id, na.rm = TRUE), # Keep as numeric
    end = max(id, na.rm = TRUE) - empty_bar_count # Keep as numeric
  ) %>%
  rowwise() %>%
  mutate(
    title_position = mean(c(start, end))
  ) %>%
  ungroup()

# --- 4. Prepare Data for Grid Lines (Optional: Value Scales) ---
max_n_value <- max(plot_data$n, na.rm = TRUE)
grid_lines_values <- c(20, 40, 60, 80, 100)
grid_lines_values <- grid_lines_values[grid_lines_values <= max_n_value]

grid_segments_data <- plot_data %>%
  group_by(community) %>%
  summarize(
    start_id = min(id, na.rm = TRUE), # Keep as numeric
    end_id = max(id, na.rm = TRUE) - empty_bar_count # Keep as numeric
  )

grid_data_final <- tibble()
for(val in grid_lines_values) {
  temp_data <- grid_segments_data %>%
    mutate(y_value = val)
  grid_data_final <- bind_rows(grid_data_final, temp_data)
}

# --- Data for grid line LABELS ---
grid_label_data <- data.frame(
  x_pos = max(plot_data$id, na.rm = TRUE) + 2, # Fixed x position outside the plot
  y_pos = grid_lines_values,
  label_text = as.character(grid_lines_values)
)

# --- 5. Make the Unified Plot ---
p <- ggplot(plot_data, aes(x = id, y = n, fill = community)) + # <--- x = id (numeric)
  # Add background grid lines for value (e.g., 20, 40, 60, 80)
  geom_segment(data = grid_data_final,
               aes(x = start_id - 0.5, y = y_value, xend = end_id + 0.5, yend = y_value),
               inherit.aes = FALSE,
               color = "grey", alpha = 0.8, linewidth = 0.3) +

  # Add text showing the value of each grid line at a fixed position
  geom_text(data = grid_label_data,
            aes(x = x_pos, y = y_pos, label = label_text),
            inherit.aes = FALSE,
            color = "grey", size = 3, angle = 0, fontface = "bold", hjust = 0) +

  # Bars for the bigrams (main plot elements)
  geom_bar(stat = "identity", alpha = 0.8, color = "white", linewidth = 0.1,
           width = 1) + # <--- Add width=1 to remove space between bars if id is numeric

  # Set limits for the y-axis, providing space for labels
  ylim(-max_n_value * 0.7, max_n_value * 1.2) +

  theme_minimal() +
  theme(
    legend.position = "none",
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(c(1.5, 1.5, 1.5, 1.5), "cm") # Top, Right, Bottom, Left margins
  ) +
  coord_polar(start = 0) +

  # Add bigram labels
  geom_text(
    data = label_data,
    aes(x = id, y = n + 10, label = bigram, hjust = hjust), # <--- x = id (numeric)
    color = "black", fontface = "bold", alpha = 0.8, size = 2.8,
    angle = label_data$angle, inherit.aes = FALSE
  ) +

  # Add base lines for each community segment
  geom_segment(
    data = base_data,
    aes(x = start - 0.5, y = -10, xend = end + 0.5, yend = -10),
    colour = "black", alpha = 0.8, linewidth = 0.6, inherit.aes = FALSE
  ) +

  # Add community group labels
  geom_text(
    data = base_data,
    aes(x = title_position, y = -40, label = paste("Comm.", community)),
    colour = "black", alpha = 0.9, size = 2, fontface = "bold", inherit.aes = FALSE
  )+
  # --- Add the Title ---
  labs(
    title = "Circular Bar Chart by Community",
    subtitle = "Frequencies of key bigrams within each community", # Updated subtitle
    caption = paste0("AT | Generated: ", Sys.Date())
  ) +
  # Apply the Set2 Brewer palette
  scale_fill_brewer(palette = "Set2") +
  # --- Customize title appearance ---
  theme(
    plot.title = element_text(hjust = 0.5, size = 16, face = "bold", margin = margin(b = 10)),
    plot.subtitle = element_text(hjust = 0.5, size = 12, margin = margin(b = 10)),
    plot.caption = element_text(hjust = 1, size = 7, color = "grey50")
  )

print(p)
```
:::

### 2.6 Community Group Membership- People & Vessels

The topic area was gathered from the bigram wordclouds and circular bar chart. The Group Name was created based on knowledge from the Members in the group and the topic area. These are the information for the 5 segmented groups:

::: panel-tabset
## The Table

```{r, echo=FALSE}
set.seed(1234)
# 6. Create a tidy summary table of members per community
grouped_members <- g_pv %>%
  as_tibble() %>%
  select(name, community) %>%
  group_by(community) %>%
  summarise(
    Members = paste(sort(name), collapse = ", "),
    .groups = "drop"
  ) %>%
  mutate(
    `Group Number` = community,
    `Topic Area` = case_when(
      community == 1 ~ "nemo reef, himark harbor, samantha blake, city council",
      community == 2 ~ "south dock, equipment transfer, security team, nemo reef, delta3, cr 7844",
      community == 3 ~ "intern reporting, conservation vessels, nemo reef",
      community == 4 ~ "10am tomorrow, 0500 tomorrow, funding channels, alternative funding",
      community == 5 ~ "classification markings, project poseidon, clearance documents, harbor security",
      TRUE ~ "Other"
    ),
    `Group Name` = case_when(
      community == 1 ~ "Conservationist Group",
      community == 2 ~ "Permit",
      community == 3 ~ "Pseudonym",
      community == 4 ~ "Suspicious",
      community == 5 ~ "Hacklee Herald",
      TRUE ~ "Miscellaneous"
    )
  ) %>%
  select(`Group Number`, `Topic Area`, `Members`, `Group Name`)

# Show the summary table in a clean format
kable(grouped_members, caption = "Community Group Membership Summary", align = "l")
```

## The Code

```{r}
#| echo: true 
#| eval: false 
set.seed(1234)
# 6. Create a tidy summary table of members per community
grouped_members <- g_pv %>%
  as_tibble() %>%
  select(name, community) %>%
  group_by(community) %>%
  summarise(
    Members = paste(sort(name), collapse = ", "),
    .groups = "drop"
  ) %>%
  mutate(
    `Group Number` = community,
    `Topic Area` = case_when(
      community == 1 ~ "nemo reef, himark harbor, samantha blake, city council",
      community == 2 ~ "south dock, equipment transfer, security team, nemo reef, delta3, cr 7844",
      community == 3 ~ "intern reporting, conservation vessels, nemo reef",
      community == 4 ~ "10am tomorrow, 0500 tomorrow, funding channels, alternative funding",
      community == 5 ~ "classification markings, project poseidon, clearance documents, harbor security",
      TRUE ~ "Other"
    ),
    `Group Name` = case_when(
      community == 1 ~ "Conservationist Group",
      community == 2 ~ "Permit",
      community == 3 ~ "Pseudonym",
      community == 4 ~ "Suspicious",
      community == 5 ~ "Hacklee Herald",
      TRUE ~ "Miscellaneous"
    )
  ) %>%
  select(`Group Number`, `Topic Area`, `Members`, `Group Name`)

# Show the summary table in a clean format
kable(grouped_members, caption = "Community Group Membership Summary", align = "l")
```
:::

::: {.callout-note title="2.6.1 Findings"}
-   Movements and changes in membership since section 1.1.2:
    -   Mako moved from Maritime to Conservationist.
    -   Samantha Blake moved from the Suspicious Characters to Conservationist.
    -   Sam and Kelly moved from their own Community to Pseudonym.
    -   The Lookout moved from Conservationist Group to Pseudonym.
    -   The Intern moved from Suspicious Characters to Pseudonym.
    -   Sailor Shift community renamed to Permit
-   From 11 nodes, we further narrowed down on the 8 nodes in the suspicious groups named:
    -   Permit (Influential Nodes: Neptune, Remora, Nadia, Davis);
    -   Conservationist Group (Influential Node: Mako);
    -   Suspicious (Influential Nodes: Mrs. Money, Boss, The Middleman).
-   We held back on the slightly less influential nodes such as: Hacklee Herald which was where Clepper Jensen worked as a journalist.
:::

### 2.7 Discussion/ Interpretation:

We mainly focused on the conversations by 8 influential nodes and some related nodes:

-   `Conservation Group` (Comm.1): Samantha Blake informed Mako to stop operations on 8 and 10th Oct. Serenity is a private luxury yacht. Osprey was likely a tourism vessel looking for charter from Mako for their tourists.

-   `Permit` (Comm. 2): Neptune, Remora, Nadia, and Davis were working on Nemo Reef operation. This referred to the Music Video Production for Sailor Shift on 14 Oct.

-   `*Pseudonym*` (Comm. 3): Other than communicating among themselves, The Lookout appeared to have also externally corresponded with Sentinel, Reef Guardian and Horizon (conservation based topics), while The Intern also externally corresponded with Mrs. Money.

-   `Suspicious` (Comm. 4): The Middleman had access to Council documents. Mrs. Money had funding from sources that would not flag out to regulators for her operations. Mrs. Money was investigating V. Miesel's structures. On 5 Oct, Boss told Mrs. Money to disguise financial trails through tourism ventures and destroy evidence of Nemo Reef operations.

-   `Hacklee Herald` (Comm. 5): Conversations between Clepper and his intern Miranda which ended on 11 Oct. Miranda mentioned an Oceanus City Council Member meeting with unmarked vessels at night.

# Question 3

### Question 3a)

### 3.1 Entities Breakdown

::: {.callout-note title="Core Logic:"}
-   If two names appear as sender and recipient in the same message, they cannot belong to the same person — i.e., they're not aliases of each other.

-   If two names sent a message at the exact time, they cannot belong to the same person.

We created Alluvial Diagrams to chart: real_identity → observed_name → community
:::

::: panel-tabset
### Extraction of the list of Entity names

```{r}
#| ehco: false 
unique_names <- sort(unique(c(other_communications_df$sender_name, 
                              other_communications_df$recipient_name)))
unique_names

```

## Manual Mapping

```{r}
name_mapping <- tibble::tibble(
  observed_name = c(
    "Boss", "City Officials", "Clepper Jensen", "Davis", "Defender", "EcoVigil",
    "Elise", "Glitters Team", "Green Guardians", "Haacklee Harbor", "Himark Harbor", "Horizon",
    "Kelly", "Knowles", "Liam Thorne", "Mako", "Marlin", "Miranda Jordan",
    "Mrs. Money", "Nadia Conti", "Neptune", "Northern Light", "Oceanus City Council", "Osprey",
    "Paackland Harbor", "Port Security", "Reef Guardian", "Remora", "Rodriguez", "Sailor Shift Team",
    "Sam", "Samantha Blake", "Seawatch", "Sentinel", "Serenity", "Small Fry",
    "The Accountant", "The Intern", "The Lookout", "The Middleman", "V. Miesel Shipping"
  ),
  real_identity = c(
    "Nadia Conti", "Oceanus City Council", "Clepper Jensen", "Captain Davis", "Sentinel", "EcoVigil",
    "Elise", "Sailor Shift Team", "Green Guardians", "Harbor Authority","Harbor Authority", "Horizon",
    "Kelly", "Knowles", "Liam Thorne", "Mako", "Small Fishing Vessel", "Miranda Jordan",
    "Elise", "Nadia Conti", "Neptune", "Commercial Vessel", "Oceanus City Council", "Tourism Vessel",
    "Harbor Authority", "Oceanus City Council", "Reef Guardian", "Remora", "Rodriguez", "Sailor Shift Team",
    "Sam", "Samantha Blake", "Kelly", "Sentinel", "Private Luxury Yacht", "Rodriguez",
    "Elise", "Sam", "Kelly", "Liam Thorne", "V. Miesel Shipping"
  ),
  community = c(
    "V. Miesel Shipping", "City Council", "Haacklee Herald", "V. Miesel Shipping", "Local Conservationist Group", "Local Conservationist Group",
    "V. Miesel Shipping", "Sailor Shift Team", "Local Conservationist Group", "Harbor Authority", "Harbor Authority", "Local Conservationist Group",
    "Local Conservationist Group", "V. Miesel Shipping", "City Council", "V. Miesel Shipping", "Maritime", "Haacklee Herald",
    "V. Miesel Shipping", "V. Miesel Shipping", "V. Miesel Shipping", "Maritime", "City Council", "Maritime",
    "Harbor Authority", "City Council", "Local Conservationist Group", "V. Miesel Shipping", "V. Miesel Shipping", "Sailor Shift Team",
    "V. Miesel Shipping", "Sailor Shift Team", "Local Conservationist Group", "Local Conservationist Group", "Maritime", "V. Miesel Shipping",
    "V. Miesel Shipping", "V. Miesel Shipping", "Local Conservationist Group", "City Council", "V. Miesel Shipping"
  )
)

multi_members <- tibble::tibble(
  observed_name = c(
    #  City Council members (additional to existing)
    "Commissioner Blake", "Commissioner Torres", "Council Knowles", "The Middleman", "Jensen from City Council", "Liam Thorne",

    # Sailor Shift Team (may already exist, but we ensure all)
    "Boss", "Council Knowles", "Davis", "Glitters Team", "Liam Thorne", "Mako", "Mrs. Money", "Nadia Conti", "Neptune",
    "Remora", "Rodriguez", "Sam", "Samantha Blake", "Small Fry", "The Accountant", "The Intern", "The Middleman", "Elise",

    #  Influential Families
    "Council Knowles", "V. Miesel Shipping",

    #  Conservationist Group
    "Defender", "EcoVigil", "Green Guardians", "Horizon", "Kelly", "Reef Guardian", "Seawatch", "Sentinel", "The Lookout"
  ),
  real_identity = c(
    "Commissioner Blake", "Commissioner Torres", "Council Knowles", "Liam Thorne", "Clepper Jensen", "Liam Thorne",

    "Nadia Conti", "Council Knowles", "Captain Davis", "Sailor Shift Team", "Liam Thorne", "Mako", "Elise", "Nadia Conti", "Neptune",
    "Remora", "Rodriguez", "Sam", "Samantha Blake", "Rodriguez", "Elise", "Sam", "Liam Thorne", "Elise",

    "Council Knowles", "V. Miesel Shipping",

    "Sentinel", "EcoVigil", "Green Guardians", "Horizon", "Kelly", "Reef Guardian", "The Lookout", "Sentinel", "Kelly"
  ),
  community = c(
    rep("City Council", 6),
    rep("Sailor Shift Team", 18),
    rep("Influential Families", 2),
    rep("Local Conservationist Group", 9)
  )
)

```
:::

### Entities- Interactive Alluvial Diagrams

Hover to see details for individual identities.

Real Identity from analysis -\> Observed Name from data -\> Community

This will probably be a drop down for each name in Shiny.

```{r}
#| echo: false
#| cold-fold: true 
#| code-summary: "Show the code"
# --- Libraries ---
library(dplyr)
library(ggplot2)
library(ggalluvial)
library(stringr)
library(plotly)

# --- 1. Build Alluvial Dataset ---
alluvial_data <- name_mapping %>%
  bind_rows(multi_members) %>% # Combine the two data sources
  distinct() %>% # Remove any duplicate rows after combining
  filter(!is.na(real_identity) & !is.na(community)) %>%
  count(real_identity, observed_name, community, name = "value") %>%
  mutate(tooltip = paste0( # Create the tooltip string
    "Real Identity: ", real_identity, "<br>",
    "Observed Name: ", observed_name, "<br>",
    "Community: ", community, "<br>",
    "Count: ", value
  ))

# --- 3. Create static ggplot object (original version) ---
p <- ggplot(alluvial_data,
            aes(axis1 = real_identity, axis2 = observed_name, axis3 = community,
                y = value,
                text = tooltip # Map the custom tooltip string to the 'text' aesthetic
            )) +
  geom_alluvium(aes(fill = real_identity), width = 1/12, alpha = 0.8) +
  geom_stratum(width = 1/12, fill = "grey90", color = "black", aes(text = NULL)) + # No dual-role fill here
  geom_text(stat = "stratum", aes(label = after_stat(stratum)), size = 3.5, hjust = 0) +
  scale_x_discrete(
    limits = c("Real Identity", "Observed Name", "Community"),
    expand = c(.05, .25)
  ) +
  labs(
    title = "All Identity Flows",
    x = NULL, y = "Link Count"
  ) +
  theme_minimal() +
  theme(
    legend.position = "none", # No legend for fill here
    panel.grid = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank(),
    plot.margin = margin(10, 80, 10, 10),
    axis.text.x = element_text(face = "bold")
  )

# --- 4. Convert to interactive Plotly object ---
# 'tooltip = "text"' tells Plotly to use the content of the 'text' aesthetic
interactive_plot <- ggplotly(p, tooltip = "text", height = 800, width = 1000)
interactive_plot # This line will print the Plotly object in  Quarto output

```

### Question 3b)

We created a graph with the character's original name, pseudonyms, and supplemented with any background information we learnt of. For instance, we learnt that Davis was a captain, or that Serenity was a private luxury yacht.Here, it is easier to determine who is using which pseudonyms by clicking on the real identity drop down panel which will then only segregate to the individual's Real Identity, Observed Name, and Community.

### Question 3c)

Understanding pseudonyms significantly reshapes our interpretation of the events in Oceanus. Without resolving aliases, the communication network appears fragmented — it may seem like dozens of separate individuals are involved. However, by mapping pseudonyms to real identities, we discover that a small number of actors are coordinating more activity than initially apparent. For example, a person using multiple pseudonyms may appear in many places at once — suggesting high influence or deception. This reveals orchestrated behavior, such as coordinated logistics, manipulation of event timelines, or masking involvement in controversial operations.

# Question 4

### Question 4a)

### 4.1 Nadia's Ego Network- Louvain community

::: panel-tabset
## Ego Network

```{r, echo=FALSE}
set.seed(1234)

# Assume g_full includes Nadia — not g from other_communications_df
g_igraph <- as.igraph(g)

# Confirm Nadia exists
if (!"Nadia Conti" %in% V(g_igraph)$name) stop("Nadia Conti not found in the graph.")

# Get ego subgraph
nadia_ego_igraph <- make_ego_graph(g_igraph, order = 1, nodes = which(V(g_igraph)$name == "Nadia Conti"), mode = "all")[[1]]

# Convert to tidygraph
nadia_ego_graph <- as_tbl_graph(nadia_ego_igraph)

# Convert to undirected for Louvain
nadia_ego_graph <- nadia_ego_graph %>% 
  to_undirected() %>% 
  activate(nodes) %>%
  mutate(
    community = group_louvain(),
    pagerank = centrality_pagerank()
  )

# Plot Nadia's ego network
ggraph(nadia_ego_graph, layout = "fr") +
  geom_edge_link(alpha = 0.4) +
  geom_node_point(aes(size = pagerank, color = as.factor(community)), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  scale_color_brewer(palette = "Set2") +
  theme_void() +
  labs(
    title = "Nadia Conti’s Ego Network",
    subtitle = "Nodes sized by PageRank, colored by Louvain community",
    color = "Community",
    size = "PageRank"
  )
```

## The Code

```{r}
#| echo: true 
#| eval: false
set.seed(1234)

# Assume g_full includes Nadia — not g from other_communications_df
g_igraph <- as.igraph(g)

# Confirm Nadia exists
if (!"Nadia Conti" %in% V(g_igraph)$name) stop("Nadia Conti not found in the graph.")

# Get ego subgraph
nadia_ego_igraph <- make_ego_graph(g_igraph, order = 1, nodes = which(V(g_igraph)$name == "Nadia Conti"), mode = "all")[[1]]

# Convert to tidygraph
nadia_ego_graph <- as_tbl_graph(nadia_ego_igraph)

# Convert to undirected for Louvain
nadia_ego_graph <- nadia_ego_graph %>% 
  to_undirected() %>% 
  activate(nodes) %>%
  mutate(
    community = group_louvain(),
    pagerank = centrality_pagerank()
  )

# Plot Nadia's ego network
ggraph(nadia_ego_graph, layout = "fr") +
  geom_edge_link(alpha = 0.4) +
  geom_node_point(aes(size = pagerank, color = as.factor(community)), alpha = 0.9) +
  geom_node_text(aes(label = name), repel = TRUE, size = 3) +
  scale_color_brewer(palette = "Set2") +
  theme_void() +
  labs(
    title = "Nadia Conti’s Ego Network",
    subtitle = "Nodes sized by PageRank, colored by Louvain community",
    color = "Community",
    size = "PageRank"
  )
```
:::

::: callout-note
-   We wanted to find out if there were sub communities within Nadia's direct network that worked closely together.
-   The orange community were possibly involved in Sailor Shifts's music video, while the green community were likely regarding ensuring compliance to authorities such as officials, the harbour and conservation team.
-   Nadia, Elise, and Marlin were the orange nodes that directly linked to the green nodes.
:::

### 4.2 Nadia's Sent and Received Ego Networks- VizNetwork

### 4.2.1 Data Preparation

::: panel-tabset
## Preparation- Nodes & Edges

```{r, echo=FALSE}
# --- 2. Clean and Prepare Nodes ---
mc3_nodes_cleaned <- mc3_nodes_raw %>%
  mutate(id = as.character(id)) %>%
  filter(!is.na(id)) %>%
  distinct(id, .keep_all = TRUE) %>%
  # Rename 'type' to 'supertype' to reduce confusion with communication type
  rename(supertype = type) %>%
  # Select only columns that are needed and are consistently present
  select(id, name, sub_type, content, timestamp) # Keep timestamp as character for now

# --- 3. Clean and Prepare Edges ---
# Rename 'type' in edges to 'edge_type' to avoid conflict with node 'supertype'
mc3_edges_cleaned <- mc3_edges_raw %>%
  rename(from_id = source,
         to_id = target,
         edge_type = type) %>% # Renamed 'type' to 'edge_type'
  mutate(across(c(from_id, to_id), as.character)) %>%
  # Filter out any edges where from_id or to_id are not in cleaned nodes
  filter(from_id %in% mc3_nodes_cleaned$id,
         to_id %in% mc3_nodes_cleaned$id)

# --- 4. Identify Nadia Conti's ID and Sub_type ---
nadia_info <- mc3_nodes_cleaned %>%
  filter(name == "Nadia Conti") %>%
  select(id, sub_type) # Corrected: Select sub_type here, not supertype

nadia_id <- nadia_info %>% pull(id)
nadia_sub_type <- nadia_info %>% pull(sub_type) # New variable for Nadia's sub_type


if (length(nadia_id) == 0) {
  stop("Nadia Conti not found in the nodes data. Please check the 'name' column or the ID.")
} else if (length(nadia_id) > 1) {
  warning("Multiple entries found for Nadia Conti. Using the first one.")
  nadia_id <- nadia_id[1]
  nadia_sub_type <- nadia_sub_type[1] # Ensure sub_type is also taken for the first one
}

print(paste("Nadia Conti's ID:", nadia_id))
print(paste("Nadia Conti's Sub_type:", nadia_sub_type))

# --- 5. Extract Nadia's Sent Communications ---
# Logic: Nadia (source) --sent--> Event_Communication (target) --received--> Recipient (target)
nadia_sent_communications <- mc3_edges_cleaned %>%
  filter(from_id == nadia_id, edge_type == "sent") %>%
  # Join with nodes to get content and timestamp of the Event_Communication node
  left_join(mc3_nodes_cleaned %>% select(id, content, timestamp),
            by = c("to_id" = "id")) %>%
  rename(event_id = to_id, event_content = content, event_timestamp = timestamp) %>%
  # Now, find the recipient of this communication event
  left_join(mc3_edges_cleaned %>%
              filter(edge_type == "received") %>%
              select(event_id_match = from_id, recipient_id = to_id),
            by = c("event_id" = "event_id_match")) %>%
  # Join with nodes to get the recipient's name AND sub_type
  left_join(mc3_nodes_cleaned %>% select(id, name, sub_type), # Select sub_type here
            by = c("recipient_id" = "id")) %>%
  rename(recipient_name = name, recipient_sub_type = sub_type) %>% # Rename sub_type
  # Select and rename final columns for sent communications
  select(
    communication_type = edge_type, # This will be "sent"
    sender_id = from_id,
    recipient_id,
    recipient_name,
    recipient_sub_type, # Include in final select
    event_id,
    content = event_content,
    timestamp = event_timestamp # Timestamp is still character here
  ) %>%
  mutate(
    sender_name = !!nadia_id, # Explicitly set sender_name to Nadia's ID/name using !!
    sender_sub_type = !!nadia_sub_type # Assign Nadia's sub_type as a constant value using !!
  )

print("--- Nadia's Sent Communications ---")
print(kable(head(nadia_sent_communications, 10), format = "markdown", align = "l"))


# --- 6. Extract Nadia's Received Communications ---
# Logic: Sender (source) --sent--> Event_Communication (target) --received--> Nadia (target)
nadia_received_communications <- mc3_edges_cleaned %>%
  filter(to_id == nadia_id, edge_type == "received") %>%
  # The source of this edge is the Event_Communication node
  rename(event_id = from_id) %>%
  # Join with nodes to get content and timestamp of the Event_Communication node
  left_join(mc3_nodes_cleaned %>% select(id, content, timestamp),
            by = c("event_id" = "id")) %>%
  rename(event_content = content, event_timestamp = timestamp) %>%
  # Now, find the original sender of this communication event
  left_join(mc3_edges_cleaned %>%
              filter(edge_type == "sent") %>%
              select(event_id_match = to_id, sender_id = from_id),
            by = c("event_id" = "event_id_match")) %>%
  # Join with nodes to get the sender's name AND sub_type
  left_join(mc3_nodes_cleaned %>% select(id, name, sub_type), # Select sub_type here
            by = c("sender_id" = "id")) %>%
  rename(sender_name = name, sender_sub_type = sub_type) %>% # Rename sub_type
  # Select and rename final columns for received communications
  select(
    communication_type = edge_type, # This will be "received"
    sender_id,
    sender_name,
    sender_sub_type, # Include in final select
    recipient_id = to_id,
    event_id,
    content = event_content,
    timestamp = event_timestamp
  ) %>%
  mutate(
    recipient_name = !!nadia_id, # Explicitly set recipient_name to Nadia's ID/name using !!
    recipient_sub_type = !!nadia_sub_type # Assign Nadia's sub_type as a constant value using !!
  )

print("--- Nadia's Received Communications ---")
print(kable(head(nadia_received_communications, 10), format = "markdown", align = "l"))

# --- 7. Combine Sent and Received Communications for Full Timeline ---
nadia_full_communications_timeline <- bind_rows(
  nadia_sent_communications,
  nadia_received_communications
) %>%
  arrange(timestamp) %>%
  # CRITICAL FIX: Explicitly convert timestamp to POSIXct after bind_rows
  # Use as.POSIXct with the observed format string
  mutate(timestamp = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S")) %>%
  # NEW: Create a sorted communicating pair for consistent coloring
  rowwise() %>% # Process row by row
  mutate(communicating_pair_sorted = paste(sort(c(sender_name, recipient_name)), collapse = "_")) %>%
  ungroup() # Return to normal data frame operations

print("--- Nadia's Full Communication Timeline (Combined) ---")
print(kable(head(nadia_full_communications_timeline, 10), format = "markdown", align = "l"))

# --- 8. Prepare Data for Ego Network Visualization (Direct Person-to-Person/Entity) ---
# Build nodes and edges directly from nadia_full_communications_timeline,
# focusing on direct sender-recipient connections.
# Nodes for the ego network graph: Collect all unique sender and recipient IDs
all_ego_person_entity_ids <- nadia_full_communications_timeline %>%
  select(id = sender_id) %>%
  bind_rows(nadia_full_communications_timeline %>% select(id = recipient_id)) %>%
  distinct(id) %>%
  filter(!is.na(id)) # Ensure no NA IDs

# Filter mc3_nodes_cleaned to get attributes for these person/entity nodes
ego_nodes_for_graph <- mc3_nodes_cleaned %>%
  filter(id %in% all_ego_person_entity_ids$id) %>%
  filter(!is.na(id)) %>% # Ensure no NA IDs in nodes for graph
  # Add attributes for visualization
  mutate(
    is_nadia = ifelse(id == nadia_id, TRUE, FALSE),
    # Create a new column for legend grouping that includes Nadia as a distinct category
    node_legend_group = ifelse(is_nadia, "Nadia Conti", sub_type),
    node_size = ifelse(is_nadia, 20, 18), # Further increased node sizes: Nadia 20, others 10
    display_name = ifelse(is_nadia, "Nadia Conti", name) # Use actual name for others
  ) %>%
  filter(!is.na(sub_type)) # Ensure nodes have a sub_type for consistent plotting

# Calculate communication counts for each node for hover text
node_comm_summary <- nadia_full_communications_timeline %>%
  group_by(id = sender_id) %>%
  summarise(sent_count = n(), .groups = 'drop') %>%
  full_join(nadia_full_communications_timeline %>%
              group_by(id = recipient_id) %>%
              summarise(received_count = n(), .groups = 'drop'),
            by = "id") %>%
  mutate(
    sent_count = replace_na(sent_count, 0),
    received_count = replace_na(received_count, 0)
  )

# Join communication summary and create hover text for nodes
ego_nodes_for_graph <- ego_nodes_for_graph %>%
  left_join(node_comm_summary, by = "id") %>%
  mutate(
    hover_text = paste(
      "Name:", display_name, "<br>",
      "Type:", node_legend_group, "<br>",
      "Sent Communications:", sent_count, "<br>",
      "Received Communications:", received_count
    )
  )

# Edges for the ego network graph: Direct Sender -> Recipient edges
# Aggregate to count occurrences for edge thickness
ego_edges_for_graph <- nadia_full_communications_timeline %>%
  # Group by sender, recipient, their names, and communication type to count interactions
  group_by(from = sender_id, to = recipient_id, sender_name, recipient_name, communication_type) %>%
  summarise(
    count_of_comm = n(), # Number of times this specific communication happened
    content_sample = paste(head(content, 1), collapse = "; "), # Sample content
    timestamp_min = min(timestamp, na.rm = TRUE),
    timestamp_max = max(timestamp, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  # Add the 'nadia_role_in_comm' column for coloring based on Nadia's perspective
  mutate(
    nadia_role_in_comm = case_when(
      from == nadia_id & communication_type == "sent" ~ "Nadia Sent",
      to == nadia_id & communication_type == "received" ~ "Nadia Received",
      TRUE ~ "Other Communication" # For communications not directly involving Nadia as sender/recipient
    )
  ) %>%
  # Ensure 'from' and 'to' are character and non-NA
  mutate(
    from = as.character(from),
    to = as.character(to)
  ) %>%
  filter(!is.na(from) & !is.na(to)) %>%
  # Filter out edges where 'from' or 'to' IDs are NOT in the final ego_nodes_for_graph
  filter(from %in% ego_nodes_for_graph$id, to %in% ego_nodes_for_graph$id) %>%
  # Create hover text for edges
  mutate(
    hover_text = paste(
      "From:", sender_name, "<br>",
      "To:", recipient_name, "<br>",
      "Type:", communication_type, "<br>",
      "Count:", count_of_comm, "<br>",
      "First:", format(timestamp_min, "%Y-%m-%d %H:%M:%S"), "<br>",
      "Last:", format(timestamp_max, "%Y-%m-%d %H:%M:%S"), "<br>",
      "Content Sample:", content_sample
    )
  )

# Create the tbl_graph object for the ego network
nadia_ego_network_graph <- tbl_graph(nodes = ego_nodes_for_graph, edges = ego_edges_for_graph, directed = TRUE)

print("--- Checking: Number of nodes and edges in Nadia's Ego Network Graph ---")
print(paste("Nodes:", gorder(nadia_ego_network_graph), "Edges:", gsize(nadia_ego_network_graph)))
print("---------------------------------------------------------------------")
```

## The Code

```{r}
#| echo: true
#| eval: false
# --- 2. Clean and Prepare Nodes ---
mc3_nodes_cleaned <- mc3_nodes_raw %>%
  mutate(id = as.character(id)) %>%
  filter(!is.na(id)) %>%
  distinct(id, .keep_all = TRUE) %>%
  # Rename 'type' to 'supertype' to reduce confusion with communication type
  rename(supertype = type) %>%
  # Select only columns that are needed and are consistently present
  select(id, name, sub_type, content, timestamp) # Keep timestamp as character for now

# --- 3. Clean and Prepare Edges ---
# Rename 'type' in edges to 'edge_type' to avoid conflict with node 'supertype'
mc3_edges_cleaned <- mc3_edges_raw %>%
  rename(from_id = source,
         to_id = target,
         edge_type = type) %>% # Renamed 'type' to 'edge_type'
  mutate(across(c(from_id, to_id), as.character)) %>%
  # Filter out any edges where from_id or to_id are not in cleaned nodes
  filter(from_id %in% mc3_nodes_cleaned$id,
         to_id %in% mc3_nodes_cleaned$id)

# --- 4. Identify Nadia Conti's ID and Sub_type ---
nadia_info <- mc3_nodes_cleaned %>%
  filter(name == "Nadia Conti") %>%
  select(id, sub_type) # Corrected: Select sub_type here, not supertype

nadia_id <- nadia_info %>% pull(id)
nadia_sub_type <- nadia_info %>% pull(sub_type) # New variable for Nadia's sub_type


if (length(nadia_id) == 0) {
  stop("Nadia Conti not found in the nodes data. Please check the 'name' column or the ID.")
} else if (length(nadia_id) > 1) {
  warning("Multiple entries found for Nadia Conti. Using the first one.")
  nadia_id <- nadia_id[1]
  nadia_sub_type <- nadia_sub_type[1] # Ensure sub_type is also taken for the first one
}

print(paste("Nadia Conti's ID:", nadia_id))
print(paste("Nadia Conti's Sub_type:", nadia_sub_type))

# --- 5. Extract Nadia's Sent Communications ---
# Logic: Nadia (source) --sent--> Event_Communication (target) --received--> Recipient (target)
nadia_sent_communications <- mc3_edges_cleaned %>%
  filter(from_id == nadia_id, edge_type == "sent") %>%
  # Join with nodes to get content and timestamp of the Event_Communication node
  left_join(mc3_nodes_cleaned %>% select(id, content, timestamp),
            by = c("to_id" = "id")) %>%
  rename(event_id = to_id, event_content = content, event_timestamp = timestamp) %>%
  # Now, find the recipient of this communication event
  left_join(mc3_edges_cleaned %>%
              filter(edge_type == "received") %>%
              select(event_id_match = from_id, recipient_id = to_id),
            by = c("event_id" = "event_id_match")) %>%
  # Join with nodes to get the recipient's name AND sub_type
  left_join(mc3_nodes_cleaned %>% select(id, name, sub_type), # Select sub_type here
            by = c("recipient_id" = "id")) %>%
  rename(recipient_name = name, recipient_sub_type = sub_type) %>% # Rename sub_type
  # Select and rename final columns for sent communications
  select(
    communication_type = edge_type, # This will be "sent"
    sender_id = from_id,
    recipient_id,
    recipient_name,
    recipient_sub_type, # Include in final select
    event_id,
    content = event_content,
    timestamp = event_timestamp # Timestamp is still character here
  ) %>%
  mutate(
    sender_name = !!nadia_id, # Explicitly set sender_name to Nadia's ID/name using !!
    sender_sub_type = !!nadia_sub_type # Assign Nadia's sub_type as a constant value using !!
  )

print("--- Nadia's Sent Communications ---")
print(kable(head(nadia_sent_communications, 10), format = "markdown", align = "l"))


# --- 6. Extract Nadia's Received Communications ---
# Logic: Sender (source) --sent--> Event_Communication (target) --received--> Nadia (target)
nadia_received_communications <- mc3_edges_cleaned %>%
  filter(to_id == nadia_id, edge_type == "received") %>%
  # The source of this edge is the Event_Communication node
  rename(event_id = from_id) %>%
  # Join with nodes to get content and timestamp of the Event_Communication node
  left_join(mc3_nodes_cleaned %>% select(id, content, timestamp),
            by = c("event_id" = "id")) %>%
  rename(event_content = content, event_timestamp = timestamp) %>%
  # Now, find the original sender of this communication event
  left_join(mc3_edges_cleaned %>%
              filter(edge_type == "sent") %>%
              select(event_id_match = to_id, sender_id = from_id),
            by = c("event_id" = "event_id_match")) %>%
  # Join with nodes to get the sender's name AND sub_type
  left_join(mc3_nodes_cleaned %>% select(id, name, sub_type), # Select sub_type here
            by = c("sender_id" = "id")) %>%
  rename(sender_name = name, sender_sub_type = sub_type) %>% # Rename sub_type
  # Select and rename final columns for received communications
  select(
    communication_type = edge_type, # This will be "received"
    sender_id,
    sender_name,
    sender_sub_type, # Include in final select
    recipient_id = to_id,
    event_id,
    content = event_content,
    timestamp = event_timestamp
  ) %>%
  mutate(
    recipient_name = !!nadia_id, # Explicitly set recipient_name to Nadia's ID/name using !!
    recipient_sub_type = !!nadia_sub_type # Assign Nadia's sub_type as a constant value using !!
  )

print("--- Nadia's Received Communications ---")
print(kable(head(nadia_received_communications, 10), format = "markdown", align = "l"))

# --- 7. Combine Sent and Received Communications for Full Timeline ---
nadia_full_communications_timeline <- bind_rows(
  nadia_sent_communications,
  nadia_received_communications
) %>%
  arrange(timestamp) %>%
  # CRITICAL FIX: Explicitly convert timestamp to POSIXct after bind_rows
  # Use as.POSIXct with the observed format string
  mutate(timestamp = as.POSIXct(timestamp, format = "%Y-%m-%d %H:%M:%S")) %>%
  # NEW: Create a sorted communicating pair for consistent coloring
  rowwise() %>% # Process row by row
  mutate(communicating_pair_sorted = paste(sort(c(sender_name, recipient_name)), collapse = "_")) %>%
  ungroup() # Return to normal data frame operations

print("--- Nadia's Full Communication Timeline (Combined) ---")
print(kable(head(nadia_full_communications_timeline, 10), format = "markdown", align = "l"))

# --- 8. Prepare Data for Ego Network Visualization (Direct Person-to-Person/Entity) ---
# Build nodes and edges directly from nadia_full_communications_timeline,
# focusing on direct sender-recipient connections.
# Nodes for the ego network graph: Collect all unique sender and recipient IDs
all_ego_person_entity_ids <- nadia_full_communications_timeline %>%
  select(id = sender_id) %>%
  bind_rows(nadia_full_communications_timeline %>% select(id = recipient_id)) %>%
  distinct(id) %>%
  filter(!is.na(id)) # Ensure no NA IDs

# Filter mc3_nodes_cleaned to get attributes for these person/entity nodes
ego_nodes_for_graph <- mc3_nodes_cleaned %>%
  filter(id %in% all_ego_person_entity_ids$id) %>%
  filter(!is.na(id)) %>% # Ensure no NA IDs in nodes for graph
  # Add attributes for visualization
  mutate(
    is_nadia = ifelse(id == nadia_id, TRUE, FALSE),
    # Create a new column for legend grouping that includes Nadia as a distinct category
    node_legend_group = ifelse(is_nadia, "Nadia Conti", sub_type),
    node_size = ifelse(is_nadia, 20, 18), # Further increased node sizes: Nadia 20, others 10
    display_name = ifelse(is_nadia, "Nadia Conti", name) # Use actual name for others
  ) %>%
  filter(!is.na(sub_type)) # Ensure nodes have a sub_type for consistent plotting

# Calculate communication counts for each node for hover text
node_comm_summary <- nadia_full_communications_timeline %>%
  group_by(id = sender_id) %>%
  summarise(sent_count = n(), .groups = 'drop') %>%
  full_join(nadia_full_communications_timeline %>%
              group_by(id = recipient_id) %>%
              summarise(received_count = n(), .groups = 'drop'),
            by = "id") %>%
  mutate(
    sent_count = replace_na(sent_count, 0),
    received_count = replace_na(received_count, 0)
  )

# Join communication summary and create hover text for nodes
ego_nodes_for_graph <- ego_nodes_for_graph %>%
  left_join(node_comm_summary, by = "id") %>%
  mutate(
    hover_text = paste(
      "Name:", display_name, "<br>",
      "Type:", node_legend_group, "<br>",
      "Sent Communications:", sent_count, "<br>",
      "Received Communications:", received_count
    )
  )

# Edges for the ego network graph: Direct Sender -> Recipient edges
# Aggregate to count occurrences for edge thickness
ego_edges_for_graph <- nadia_full_communications_timeline %>%
  # Group by sender, recipient, their names, and communication type to count interactions
  group_by(from = sender_id, to = recipient_id, sender_name, recipient_name, communication_type) %>%
  summarise(
    count_of_comm = n(), # Number of times this specific communication happened
    content_sample = paste(head(content, 1), collapse = "; "), # Sample content
    timestamp_min = min(timestamp, na.rm = TRUE),
    timestamp_max = max(timestamp, na.rm = TRUE),
    .groups = 'drop'
  ) %>%
  # Add the 'nadia_role_in_comm' column for coloring based on Nadia's perspective
  mutate(
    nadia_role_in_comm = case_when(
      from == nadia_id & communication_type == "sent" ~ "Nadia Sent",
      to == nadia_id & communication_type == "received" ~ "Nadia Received",
      TRUE ~ "Other Communication" # For communications not directly involving Nadia as sender/recipient
    )
  ) %>%
  # Ensure 'from' and 'to' are character and non-NA
  mutate(
    from = as.character(from),
    to = as.character(to)
  ) %>%
  filter(!is.na(from) & !is.na(to)) %>%
  # Filter out edges where 'from' or 'to' IDs are NOT in the final ego_nodes_for_graph
  filter(from %in% ego_nodes_for_graph$id, to %in% ego_nodes_for_graph$id) %>%
  # Create hover text for edges
  mutate(
    hover_text = paste(
      "From:", sender_name, "<br>",
      "To:", recipient_name, "<br>",
      "Type:", communication_type, "<br>",
      "Count:", count_of_comm, "<br>",
      "First:", format(timestamp_min, "%Y-%m-%d %H:%M:%S"), "<br>",
      "Last:", format(timestamp_max, "%Y-%m-%d %H:%M:%S"), "<br>",
      "Content Sample:", content_sample
    )
  )

# Create the tbl_graph object for the ego network
nadia_ego_network_graph <- tbl_graph(nodes = ego_nodes_for_graph, edges = ego_edges_for_graph, directed = TRUE)

print("--- Checking: Number of nodes and edges in Nadia's Ego Network Graph ---")
print(paste("Nodes:", gorder(nadia_ego_network_graph), "Edges:", gsize(nadia_ego_network_graph)))
print("---------------------------------------------------------------------")
```
:::

### 4.2.2 Nadia's Sent and Received Ego Networks

### 4.2.2.1 Sent Communications Network

::: no-code-fold
```{r, echo=FALSE}

# Define custom colors for node types (reusing from previous code)
node_legend_colors_plot <- c(
  "Person" = "#88CCEE",      # Blue
  "Vessel" = "#D55E00",      # Orange
  "Organization" = "#117733", # Green
  "Location" = "#AA4499",   # Purple
  "Nadia Conti" = "red"      # Special color for Nadia
)

# Define custom shapes for node subtypes
node_legend_shapes_plot <- c(
  "Person" = "dot",        # Circle for visNetwork
  "Vessel" = "triangle",
  "Organization" = "square",
  "Location" = "diamond",
  "Nadia Conti" = "star"   # Star shape for Nadia in visNetwork
)

# Separate the edges into two sets: Nadia Sent and Nadia Received
edges_sent <- ego_edges_for_graph %>%
  filter(nadia_role_in_comm == "Nadia Sent")

edges_received <- ego_edges_for_graph %>%
  filter(nadia_role_in_comm == "Nadia Received")

# Function to build visNetwork plot for a given edge set
build_visnetwork_plot <- function(edge_df, title_label) {
  # Prepare nodes from edge list
  node_ids <- unique(c(edge_df$from, edge_df$to))

  nodes <- ego_nodes_for_graph %>%
    filter(id %in% node_ids) %>%
    mutate(
      label = ifelse(display_name == "Nadia Conti", "", display_name),
      title = paste0(
        "<b>", display_name, "</b><br>",
        "Type: ", node_legend_group, "<br>",
        "Sent: ", sent_count, "<br>",
        "Received: ", received_count
      ),
      group = ifelse(display_name == "Nadia Conti", "Nadia Conti", node_legend_group)
    ) %>%
    select(id, label, title, group, value = node_size)

  # Prepare edges with arrow and tooltip
  edges <- edge_df %>%
    filter(!is.na(from) & !is.na(to)) %>%
    mutate(
      arrows = "to",
      title = paste0(
        "<b>From:</b> ", sender_name, "<br>",
        "<b>To:</b> ", recipient_name, "<br>",
        "<b>Type:</b> ", communication_type, "<br>",
        "<b>Count:</b> ", count_of_comm, "<br>",
        "<b>First:</b> ", format(timestamp_min, "%Y-%m-%d %H:%M:%S"), "<br>",
        "<b>Last:</b> ", format(timestamp_max, "%Y-%m-%d %H:%M:%S"), "<br>",
      "<b>Content Sample:</b><br><div style='max-width:300px;white-space:normal;'>", content_sample, "</div>"
      )
    ) %>%
    select(from, to, arrows, title, width = count_of_comm)

  # Create visNetwork
  visNetwork(nodes, edges, width = "100%", height = "600px") %>%
    visEdges(smooth = FALSE, arrows = list(to = list(enabled = TRUE, scaleFactor = 1.5))) %>%
    visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
    visIgraphLayout(layout = "layout_with_fr") %>%
    visNodes(font = list(size = 14)) %>%
    visGroups(groupname = "Person", color = node_legend_colors_plot[["Person"]], shape = node_legend_shapes_plot[["Person"]]) %>%
    visGroups(groupname = "Vessel", color = node_legend_colors_plot[["Vessel"]], shape = node_legend_shapes_plot[["Vessel"]]) %>%
    visGroups(groupname = "Organization", color = node_legend_colors_plot[["Organization"]], shape = node_legend_shapes_plot[["Organization"]]) %>%
    visGroups(groupname = "Location", color = node_legend_colors_plot[["Location"]], shape = node_legend_shapes_plot[["Location"]]) %>%
    visGroups(groupname = "Nadia Conti", color = node_legend_colors_plot[["Nadia Conti"]], shape = node_legend_shapes_plot[["Nadia Conti"]]) %>%
      visLegend(
    addNodes = legend_df,
    ncol = 2,
    position = "left",
    main = "Entity (Sub)Types",
    useGroups = FALSE) %>%
    visLayout(randomSeed = 123) %>%
    visNetwork::visExport() %>%
    visNetwork::visPhysics(enabled = TRUE) %>%
    visNetwork::visInteraction(navigationButtons = TRUE) %>%
    visNetwork::visEvents(stabilizationIterationsDone = "function () {this.setOptions({physics:false});}")
}

# Build and show visNetwork plots
build_visnetwork_plot(edges_sent, "Nadia Sent Ego Network")
```
:::

```{r}
#| code-fold: true
#| code-summary: "Show the code"
# Define custom colors for node types (reusing from previous code)
node_legend_colors_plot <- c(
  "Person" = "#88CCEE",      # Blue
  "Vessel" = "#D55E00",      # Orange
  "Organization" = "#117733", # Green
  "Location" = "#AA4499",   # Purple
  "Nadia Conti" = "red"      # Special color for Nadia
)

# Define custom shapes for node subtypes
node_legend_shapes_plot <- c(
  "Person" = "dot",        # Circle for visNetwork
  "Vessel" = "triangle",
  "Organization" = "square",
  "Location" = "diamond",
  "Nadia Conti" = "star"   # Star shape for Nadia in visNetwork
)

# Separate the edges into two sets: Nadia Sent and Nadia Received
edges_sent <- ego_edges_for_graph %>%
  filter(nadia_role_in_comm == "Nadia Sent")

edges_received <- ego_edges_for_graph %>%
  filter(nadia_role_in_comm == "Nadia Received")

# Function to build visNetwork plot for a given edge set
build_visnetwork_plot <- function(edge_df, title_label) {
  # Prepare nodes from edge list
  node_ids <- unique(c(edge_df$from, edge_df$to))

  nodes <- ego_nodes_for_graph %>%
    filter(id %in% node_ids) %>%
    mutate(
      label = ifelse(display_name == "Nadia Conti", "", display_name),
      title = paste0(
        "<b>", display_name, "</b><br>",
        "Type: ", node_legend_group, "<br>",
        "Sent: ", sent_count, "<br>",
        "Received: ", received_count
      ),
      group = ifelse(display_name == "Nadia Conti", "Nadia Conti", node_legend_group)
    ) %>%
    select(id, label, title, group, value = node_size)

  # Prepare edges with arrow and tooltip
  edges <- edge_df %>%
    filter(!is.na(from) & !is.na(to)) %>%
    mutate(
      arrows = "to",
      title = paste0(
        "<b>From:</b> ", sender_name, "<br>",
        "<b>To:</b> ", recipient_name, "<br>",
        "<b>Type:</b> ", communication_type, "<br>",
        "<b>Count:</b> ", count_of_comm, "<br>",
        "<b>First:</b> ", format(timestamp_min, "%Y-%m-%d %H:%M:%S"), "<br>",
        "<b>Last:</b> ", format(timestamp_max, "%Y-%m-%d %H:%M:%S"), "<br>",
      "<b>Content Sample:</b><br><div style='max-width:300px;white-space:normal;'>", content_sample, "</div>"
      )
    ) %>%
    select(from, to, arrows, title, width = count_of_comm)

  # Create visNetwork
  visNetwork(nodes, edges, width = "100%", height = "600px") %>%
    visEdges(smooth = FALSE, arrows = list(to = list(enabled = TRUE, scaleFactor = 1.5))) %>%
    visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
    visIgraphLayout(layout = "layout_with_fr") %>%
    visNodes(font = list(size = 14)) %>%
    visGroups(groupname = "Person", color = node_legend_colors_plot[["Person"]], shape = node_legend_shapes_plot[["Person"]]) %>%
    visGroups(groupname = "Vessel", color = node_legend_colors_plot[["Vessel"]], shape = node_legend_shapes_plot[["Vessel"]]) %>%
    visGroups(groupname = "Organization", color = node_legend_colors_plot[["Organization"]], shape = node_legend_shapes_plot[["Organization"]]) %>%
    visGroups(groupname = "Location", color = node_legend_colors_plot[["Location"]], shape = node_legend_shapes_plot[["Location"]]) %>%
    visGroups(groupname = "Nadia Conti", color = node_legend_colors_plot[["Nadia Conti"]], shape = node_legend_shapes_plot[["Nadia Conti"]]) %>%
      visLegend(
    addNodes = legend_df,
    ncol = 2,
    position = "left",
    main = "Entity (Sub)Types",
    useGroups = FALSE) %>%
    visLayout(randomSeed = 123) %>%
    visNetwork::visExport() %>%
    visNetwork::visPhysics(enabled = TRUE) %>%
    visNetwork::visInteraction(navigationButtons = TRUE) %>%
    visNetwork::visEvents(stabilizationIterationsDone = "function () {this.setOptions({physics:false});}")
}

# Build and show visNetwork plots
build_visnetwork_plot(edges_sent, "Nadia Sent Ego Network")
```

### 4.2.2.2 Received Communications Network

::: no-code-fold
```{r, echo=FALSE}

build_visnetwork_plot(edges_received, "Nadia Received Ego Network")
```
:::

```{r, results=FALSE}
#| code-fold: true
#| code-summary: "Show the code"
build_visnetwork_plot(edges_received, "Nadia Received Ego Network")
```

::: {.callout-note title="4.2.3 Findings"}
We then wanted to find more about the correspondences. The first graph illustrated Nadia's sent communications and the second graph were her received communications. Hover over nodes to see the sent or received count from the perspective of the entity. Hover over arrowheads to see the number, direction, count, first and last correspondence time, type of sent or received, and content of one communication. Nadia sent only 8 but received 18 communications (possibly indicative of using a pseudonym):

-   Nodes involved: Nadia, Davis, Elise, Haacklee Habor, Liam, Marlin, Neptune, Oceanus City Council, Remora, Rodriguez, Sailor Shifts Team, Sentinel, V. Miesel Shipping.

-   Sent more direct communications to Liam (2) and Neptune (2), relative to others.

-   Received more from Davis (5), Elise (3), and Liam (2), relative to others.

-   The next step would be to find out the suspicious characters/ activities.
:::

### 4.3 Nadia's Ego Network: 3-hops degree centrality

To uncover more details, we designed n-hops degree centrality here. We input 3 hops to hover over the nodes and look into the communications in a wider network. 3-hop exposes overlapping communites (Nadia communicating with someone who coordinates between groups). The "bridges" may show their value in 3-hops. It also increases the change of detecting complete or near complete cliques. We understand that should there be requirements for details, we could look into n-hops and more.

::: no-code-fold
```{r, echo=FALSE}
#| code-fold: true
#| code-summary: "Show the code"


# --- Define event and relationship subtypes (optional, for filtering or labeling) ---
event_subtypes <- c(
  "Communication", "Monitoring", "VesselMovement", "Assessment",
  "Collaborate", "Endorsement", "TourActivity", "TransponderPing",
  "Harbor Report", "Fishing", "Criticize"
)

relationship_subtypes <- c(
  "Coordinates", "AccessPermission", "Operates", "Colleagues",
  "Suspicious", "Reports", "Jurisdiction", "Unfriendly", "Friends"
)

# --- Define node colors and shapes by type or key sub-type ---
node_legend_colors_plot <- c(
  "Person" = "#88CCEE",
  "Vessel" = "#D55E00",
  "Organization" = "#117733",
  "Location" = "#AA4499",
  "Group" = "#CC79A7",
  "Event" = "#DDCC77",
  "Relationship" = "#AF8DC3"
)

node_legend_shapes_plot <- c(
  "Person" = "dot",
  "Vessel" = "triangle",
  "Organization" = "square",
  "Location" = "diamond",
  "Group" = "circle",
  "Event" = "star",
  "Relationship" = "square"
)

STYLES <- list(
  node_label_dark = "black",
  font_family = "Roboto Condensed"
)

# ---- 2. Define function to extract ego subgraph ----
extract_ego_subgraph <- function(center_node = "Nadia Conti", hops = 3) {
  # Construct igraph object
  g <- graph_from_data_frame(
    d = mc3_edges_final %>% select(from = from_id, to = to_id),
    vertices = mc3_nodes_final %>% select(id) %>% distinct() %>% rename(name = id),
    directed = TRUE
  )

  # Extract ego network
  ego_graph <- make_ego_graph(g, order = hops, nodes = center_node, mode = "all")[[1]]
  node_ids <- V(ego_graph)$name
  edge_df <- as_data_frame(ego_graph, what = "edges")

  # Prepare node metadata for visNetwork
  ego_nodes <- mc3_nodes_final %>%
    filter(id %in% node_ids) %>%
    mutate(
      label = ifelse(is.na(name), id, name),
      tooltip_extra = case_when(
        type == "Event" & sub_type == "Communication" ~ content,
        type == "Event" & sub_type == "Monitoring" ~ findings,
        type == "Event" & sub_type == "VesselMovement" ~ destination,
        type == "Event" & sub_type == "Assessment" ~ results,
        type == "Relationship" & sub_type == "Coordinates" ~ coordination_type,
        type == "Relationship" & sub_type == "Operates" ~ operational_role,
        type == "Relationship" & sub_type == "Jurisdiction" ~ jurisdiction_type,
        TRUE ~ NA_character_
      ),
      title = paste0(
        "<b>", label, "</b><br>",
        "Type: ", type, "<br>",
        "Sub-type: ", sub_type, "<br>",
        ifelse(!is.na(tooltip_extra), paste0("<br><b>Details:</b> ", tooltip_extra), "")
      ),
      group = case_when(
        sub_type %in% names(node_legend_colors_plot) ~ sub_type,
        type %in% names(node_legend_colors_plot) ~ type,
        TRUE ~ "Other"
      )
    ) %>%
    select(id, label, group, title) %>%
    distinct(id, .keep_all = TRUE)

  list(nodes = ego_nodes, edges = edge_df)
}

# ---- 3. Extract Nadia Conti's 3-hop ego network ----
ego_data <- extract_ego_subgraph("Nadia Conti", hops = 3)
nodes <- ego_data$nodes
edges <- ego_data$edges

# (Optional) Save output
nadia_ego_nodes_2hop <- nodes
nadia_ego_edges_2hop <- edges

# ---- 4. Build visNetwork plot ----
net <- visNetwork(nodes, edges, width = "100%", height = "600px") %>%
  visEdges(arrows = list(to = list(enabled = TRUE, scaleFactor = 1.5))) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visNodes(font = list(
    size = 14,
    color = STYLES$node_label_dark,
    face = STYLES$font_family,
    vadjust = -15
  ))

# ---- 5. Apply color/shape for known groups ----
used_groups <- intersect(unique(nodes$group), names(node_legend_colors_plot))

for (group_name in used_groups) {
  net <- net %>% visGroups(
    groupname = group_name,
    color = node_legend_colors_plot[[group_name]],
    shape = node_legend_shapes_plot[[group_name]]
  )
}

# ---- 6. Add legend dynamically ----
legend_df <- tibble::tibble(
  label = used_groups,
  shape = node_legend_shapes_plot[used_groups],
  color = node_legend_colors_plot[used_groups]
) %>%
  distinct(label, .keep_all = TRUE)

net <- net %>% visLegend(
  addNodes = legend_df,
  ncol = 2,
  position = "left",
  main = "Entity (Sub)Types",
  useGroups = FALSE
)

# ---- 7. Render the network ----
net



```
:::

```{r, results=FALSE}
#| code-fold: true
#| code-summary: "Show the code"

# --- Define event and relationship subtypes (optional, for filtering or labeling) ---
event_subtypes <- c(
  "Communication", "Monitoring", "VesselMovement", "Assessment",
  "Collaborate", "Endorsement", "TourActivity", "TransponderPing",
  "Harbor Report", "Fishing", "Criticize"
)

relationship_subtypes <- c(
  "Coordinates", "AccessPermission", "Operates", "Colleagues",
  "Suspicious", "Reports", "Jurisdiction", "Unfriendly", "Friends"
)

# --- Define node colors and shapes by type or key sub-type ---
node_legend_colors_plot <- c(
  "Person" = "#88CCEE",
  "Vessel" = "#D55E00",
  "Organization" = "#117733",
  "Location" = "#AA4499",
  "Group" = "#CC79A7",
  "Event" = "#DDCC77",
  "Relationship" = "#AF8DC3"
)

node_legend_shapes_plot <- c(
  "Person" = "dot",
  "Vessel" = "triangle",
  "Organization" = "square",
  "Location" = "diamond",
  "Group" = "circle",
  "Event" = "star",
  "Relationship" = "square"
)

STYLES <- list(
  node_label_dark = "black",
  font_family = "Roboto Condensed"
)

# ---- 2. Define function to extract ego subgraph ----
extract_ego_subgraph <- function(center_node = "Nadia Conti", hops = 3) {
  # Construct igraph object
  g <- graph_from_data_frame(
    d = mc3_edges_final %>% select(from = from_id, to = to_id),
    vertices = mc3_nodes_final %>% select(id) %>% distinct() %>% rename(name = id),
    directed = TRUE
  )

  # Extract ego network
  ego_graph <- make_ego_graph(g, order = hops, nodes = center_node, mode = "all")[[1]]
  node_ids <- V(ego_graph)$name
  edge_df <- as_data_frame(ego_graph, what = "edges")

  # Prepare node metadata for visNetwork
  ego_nodes <- mc3_nodes_final %>%
    filter(id %in% node_ids) %>%
    mutate(
      label = ifelse(is.na(name), id, name),
      tooltip_extra = case_when(
        type == "Event" & sub_type == "Communication" ~ content,
        type == "Event" & sub_type == "Monitoring" ~ findings,
        type == "Event" & sub_type == "VesselMovement" ~ destination,
        type == "Event" & sub_type == "Assessment" ~ results,
        type == "Relationship" & sub_type == "Coordinates" ~ coordination_type,
        type == "Relationship" & sub_type == "Operates" ~ operational_role,
        type == "Relationship" & sub_type == "Jurisdiction" ~ jurisdiction_type,
        TRUE ~ NA_character_
      ),
      title = paste0(
        "<b>", label, "</b><br>",
        "Type: ", type, "<br>",
        "Sub-type: ", sub_type, "<br>",
        ifelse(!is.na(tooltip_extra), paste0("<br><b>Details:</b> ", tooltip_extra), "")
      ),
      group = case_when(
        sub_type %in% names(node_legend_colors_plot) ~ sub_type,
        type %in% names(node_legend_colors_plot) ~ type,
        TRUE ~ "Other"
      )
    ) %>%
    select(id, label, group, title) %>%
    distinct(id, .keep_all = TRUE)

  list(nodes = ego_nodes, edges = edge_df)
}

# ---- 3. Extract Nadia Conti's 3-hop ego network ----
ego_data <- extract_ego_subgraph("Nadia Conti", hops = 3)
nodes <- ego_data$nodes
edges <- ego_data$edges

# (Optional) Save output
nadia_ego_nodes_2hop <- nodes
nadia_ego_edges_2hop <- edges

# ---- 4. Build visNetwork plot ----
net <- visNetwork(nodes, edges, width = "100%", height = "600px") %>%
  visEdges(arrows = list(to = list(enabled = TRUE, scaleFactor = 1.5))) %>%
  visOptions(highlightNearest = TRUE, nodesIdSelection = TRUE) %>%
  visIgraphLayout(layout = "layout_with_fr") %>%
  visNodes(font = list(
    size = 14,
    color = STYLES$node_label_dark,
    face = STYLES$font_family,
    vadjust = -15
  ))

# ---- 5. Apply color/shape for known groups ----
used_groups <- intersect(unique(nodes$group), names(node_legend_colors_plot))

for (group_name in used_groups) {
  net <- net %>% visGroups(
    groupname = group_name,
    color = node_legend_colors_plot[[group_name]],
    shape = node_legend_shapes_plot[[group_name]]
  )
}

# ---- 6. Add legend dynamically ----
legend_df <- tibble::tibble(
  label = used_groups,
  shape = node_legend_shapes_plot[used_groups],
  color = node_legend_colors_plot[used_groups]
) %>%
  distinct(label, .keep_all = TRUE)

net <- net %>% visLegend(
  addNodes = legend_df,
  ncol = 2,
  position = "left",
  main = "Entity (Sub)Types",
  useGroups = FALSE
)

# ---- 7. Render the network ----
net


```

::: {.callout-note title="4.3.1 Findings"}
-   Nodes from 1-hop: Nadia, Davis, Elise, Haacklee Habor, Liam, Marlin, Neptune, Oceanus City Council, Remora, Rodriguez, Sailor Shifts Team, Sentinel, V. Miesel Shipping.

-   Additional nodes from 3-hop: Conservation vessels, EcoVigil, Sam, The Accountant, Mako, Nemo Reef.

-   We would then use these 3-hop nodes to drill in deeper to find suspicious relationships between nodes.
:::

### Question 4b)

### 4.4 Summary of Nadia's Actions

### 4.4.1 Sequential Timeline in Table (3-hop)

::: panel-tabset
## The Suspicious Entities

```{r, echo=FALSE}
# Extract Nadia Conti's 3-hop ego network

# ---- Step 1: Create igraph from edge list ----
g <- graph_from_data_frame(
  d = mc3_edges_final %>% select(from = from_id, to = to_id),
  vertices = mc3_nodes_final %>% select(id) %>% distinct() %>% rename(name = id),
  directed = TRUE
)

# ---- Step 2: Extract 3-hop ego network for Nadia Conti ----
ego_graph <- make_ego_graph(g, order = 3, nodes = "Nadia Conti", mode = "all")[[1]]
node_ids <- V(ego_graph)$name
edge_df <- as_data_frame(ego_graph, what = "edges")

# ---- Step 3: Enrich ego nodes with labels and metadata ----
nadia_ego_nodes_3hop <- mc3_nodes_final %>%
  filter(id %in% node_ids) %>%
  mutate(
    label = ifelse(is.na(name), id, name),
    tooltip_extra = case_when(
      type == "Event" & sub_type == "Communication" ~ content,
      type == "Event" & sub_type == "Monitoring" ~ findings,
      type == "Event" & sub_type == "VesselMovement" ~ destination,
      type == "Event" & sub_type == "Assessment" ~ results,
      type == "Relationship" & sub_type == "Coordinates" ~ coordination_type,
      type == "Relationship" & sub_type == "Operates" ~ operational_role,
      type == "Relationship" & sub_type == "Jurisdiction" ~ jurisdiction_type,
      TRUE ~ NA_character_
    )
  )

# ---- Step 4: Enrich edges with sender/recipient names and types ----
nadia_ego_edges_3hop <- edge_df %>%
  left_join(nadia_ego_nodes_3hop %>% select(id, sender_name = label, sender_sub_type = sub_type), by = c("from" = "id")) %>%
  left_join(nadia_ego_nodes_3hop %>% select(id, recipient_name = label, recipient_sub_type = sub_type), by = c("to" = "id"))

# ---- Step 5: Create detailed communication dataframe ----
nadia_ego_comm_df_3hop <- edge_df %>%
  left_join(
    nadia_ego_nodes_3hop %>%
      select(id, name, sub_type),
    by = c("from" = "id")
  ) %>%
  rename(
    sender_id = from,
    sender_name = name,
    sender_type = sub_type
  ) %>%
  left_join(
    nadia_ego_nodes_3hop %>%
      select(id, name, sub_type, content, findings, destination, results,
             coordination_type, operational_role, jurisdiction_type, timestamp),
    by = c("to" = "id")
  ) %>%
  rename(
    recipient_id = to,
    recipient_name = name,
    recipient_type = sub_type
  ) %>%
  mutate(
    details = coalesce(content, findings, destination, results,
                       coordination_type, operational_role, jurisdiction_type),
    timestamp = suppressWarnings(ymd_hms(timestamp))
  ) %>%
  select(
    sender_id, sender_name, sender_type,
    recipient_id, recipient_name, recipient_type,
    timestamp, details
  )

# ---- Step 6: Filter for 'suspicious' in any relevant field ----
suspicious_links <- nadia_ego_comm_df_3hop %>%
  filter(
    grepl("suspicious", sender_id, ignore.case = TRUE) |
    grepl("suspicious", sender_type, ignore.case = TRUE) |
    grepl("suspicious", recipient_id, ignore.case = TRUE) |
    grepl("suspicious", recipient_type, ignore.case = TRUE)
  ) %>%
  select(
    sender_id, sender_name, sender_type,
    recipient_id, recipient_name, recipient_type
  )


# ---- Step 7: View suspicious interactions ----
unique_ids <- unique(c(suspicious_links$sender_id, suspicious_links$recipient_id))
print(unique_ids)

```

## The Code

```{r}
#| echo: true
#| eval: false
# Extract Nadia Conti's 3-hop ego network
#| code-fold: true
#| code-summary: "Show the code"

# ---- Step 1: Create igraph from edge list ----
g <- graph_from_data_frame(
  d = mc3_edges_final %>% select(from = from_id, to = to_id),
  vertices = mc3_nodes_final %>% select(id) %>% distinct() %>% rename(name = id),
  directed = TRUE
)

# ---- Step 2: Extract 3-hop ego network for Nadia Conti ----
ego_graph <- make_ego_graph(g, order = 3, nodes = "Nadia Conti", mode = "all")[[1]]
node_ids <- V(ego_graph)$name
edge_df <- as_data_frame(ego_graph, what = "edges")

# ---- Step 3: Enrich ego nodes with labels and metadata ----
nadia_ego_nodes_3hop <- mc3_nodes_final %>%
  filter(id %in% node_ids) %>%
  mutate(
    label = ifelse(is.na(name), id, name),
    tooltip_extra = case_when(
      type == "Event" & sub_type == "Communication" ~ content,
      type == "Event" & sub_type == "Monitoring" ~ findings,
      type == "Event" & sub_type == "VesselMovement" ~ destination,
      type == "Event" & sub_type == "Assessment" ~ results,
      type == "Relationship" & sub_type == "Coordinates" ~ coordination_type,
      type == "Relationship" & sub_type == "Operates" ~ operational_role,
      type == "Relationship" & sub_type == "Jurisdiction" ~ jurisdiction_type,
      TRUE ~ NA_character_
    )
  )

# ---- Step 4: Enrich edges with sender/recipient names and types ----
nadia_ego_edges_3hop <- edge_df %>%
  left_join(nadia_ego_nodes_3hop %>% select(id, sender_name = label, sender_sub_type = sub_type), by = c("from" = "id")) %>%
  left_join(nadia_ego_nodes_3hop %>% select(id, recipient_name = label, recipient_sub_type = sub_type), by = c("to" = "id"))

# ---- Step 5: Create detailed communication dataframe ----
nadia_ego_comm_df_3hop <- edge_df %>%
  left_join(
    nadia_ego_nodes_3hop %>%
      select(id, name, sub_type),
    by = c("from" = "id")
  ) %>%
  rename(
    sender_id = from,
    sender_name = name,
    sender_type = sub_type
  ) %>%
  left_join(
    nadia_ego_nodes_3hop %>%
      select(id, name, sub_type, content, findings, destination, results,
             coordination_type, operational_role, jurisdiction_type, timestamp),
    by = c("to" = "id")
  ) %>%
  rename(
    recipient_id = to,
    recipient_name = name,
    recipient_type = sub_type
  ) %>%
  mutate(
    details = coalesce(content, findings, destination, results,
                       coordination_type, operational_role, jurisdiction_type),
    timestamp = suppressWarnings(ymd_hms(timestamp))
  ) %>%
  select(
    sender_id, sender_name, sender_type,
    recipient_id, recipient_name, recipient_type,
    timestamp, details
  )

# ---- Step 6: Filter for 'suspicious' in any relevant field ----
suspicious_links <- nadia_ego_comm_df_3hop %>%
  filter(
    grepl("suspicious", sender_id, ignore.case = TRUE) |
    grepl("suspicious", sender_type, ignore.case = TRUE) |
    grepl("suspicious", recipient_id, ignore.case = TRUE) |
    grepl("suspicious", recipient_type, ignore.case = TRUE)
  ) %>%
  select(
    sender_id, sender_name, sender_type,
    recipient_id, recipient_name, recipient_type
  )


# ---- Step 7: View suspicious interactions ----
unique_ids <- unique(c(suspicious_links$sender_id, suspicious_links$recipient_id))
print(unique_ids)
```
:::

-   Elise, EcoVigil, Elise, Davis, Liam, Mako, Neptune, Sam, Remora, Rodriguez, Sailor Shifts Team, Sentinel, The Accountant, Oceanus City Council, V. Miesel Shipping possibly found something suspicious or were involved in something suspicious.

### 4.4.2 Plotted Timeline (3-hop)- Only suspicious communications

These are the suspicious communications extracted from 4.4.1.

```{r}
#| code-fold: true
#| code-summary: "Show the code"

# ---- Step 1: Define fixed suspicious Event_Communication IDs ----
event_ids_to_extract <- c(
  "Event_Communication_222", "Event_Communication_270",
  "Event_Communication_272", "Event_Communication_370",
  "Event_Communication_485", "Event_Communication_535",
  "Event_Communication_565", "Event_Communication_574",
  "Event_Communication_601", "Event_Communication_612",
  "Event_Communication_639", "Event_Communication_677",
  "Event_Communication_724", "Event_Communication_726",
  "Event_Communication_753", "Event_Communication_761",
  "Event_Communication_833", "Event_Communication_916",
  "Event_Communication_951"
)

# ---- Step 2: Match to master communication events ----
matched_comms_df <- other_communications_df %>%
  filter(event_id %in% event_ids_to_extract)

# ---- Step 3: Prepare data for plotting ----
matched_comms_df_for_plot <- matched_comms_df %>%
  mutate(
    timestamp = as.POSIXct(timestamp),
    comm_date = as.Date(timestamp),
    comm_time_of_day = hms::as_hms(format(timestamp, "%H:%M:%S")),
    sender_sub_type = factor(sender_sub_type, levels = c("Person", "Vessel", "Organization", "Location")),
    communicating_pair_sorted = paste(pmin(sender_name, recipient_name), pmax(sender_name, recipient_name), sep = " & ")
  )

# ---- Step 4: Add tooltip labels ----
plot_data <- matched_comms_df_for_plot %>%
  mutate(
    wrapped_content = str_wrap(content, width = 50),
    tooltip_text = paste0(
      "<b>Date:</b> ", comm_date, "<br>",
      "<b>Time:</b> ", format(comm_time_of_day, "%H:%M:%S"), "<br>",
      "<b>Event ID:</b> ", event_id, "<br><br>",
      "<b>From:</b> ", sender_name, "<br>",
      "<b>To:</b> ", recipient_name, "<br><br>",
      "<b>Content:</b><br>", wrapped_content
    )
  )

# ---- Step 5: Generate timeline plot ----
p <- ggplot(plot_data, aes(x = comm_date, y = comm_time_of_day)) +
  geom_point(aes(
    color = sender_name,
    shape = sender_sub_type,
    text = tooltip_text
  ), show.legend = c(color = TRUE, shape = FALSE), size = 2, alpha = 0.7) +

  scale_shape_manual(values = c(
    "Person" = 16,
    "Vessel" = 17,
    "Organization" = 15,
    "Location" = 18
  )) +

  scale_y_time(
    limits = hms::as_hms(c("08:00:00", "14:00:00")),
    breaks = hms::as_hms(c("08:00:00", "09:00:00", "10:00:00", "11:00:00", "12:00:00", "13:00:00", "14:00:00")),
    labels = c("08:00", "09:00", "10:00", "11:00", "12:00", "13:00", "14:00")
  ) +

  scale_x_date(
    date_breaks = "1 day",
    date_labels = "%d %b"
  ) +

  facet_wrap(~ sender_sub_type, ncol = 1, scales = "fixed") +

  labs(
    title = "Suspicious Communications Timeline (Nadia's 3-hop Ego Network)",
    x = "Date",
    y = "Time of Day",
    color = "Sender"
  ) +

  theme_grey() +
  theme(
    axis.text.y = element_text(size = 6),
    axis.title.y = element_text(size = 7),
    axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 10), size = 7),
    panel.spacing = unit(0.5, "lines"),
    strip.text = element_text(size = 8, face = "bold"),
    legend.position = "bottom",
    legend.text = element_text(size = 6),
    legend.title = element_text(size = 7)
  )

# ---- Step 6: Convert to interactive plot ----
ggplotly(p, tooltip = "text")

```

### Plotted Timeline (3-hop)- Full communications

```{r}
#| code-fold: true
#| code-summary: "Show the code"

# ---- Step 1: Extract Communication Event IDs from Nadia's 3-hop ego network ----
event_ids_to_extract <- nadia_ego_comm_df_3hop %>%
  filter(str_starts(sender_id, "Event_Communication_")) %>%
  pull(sender_id) %>%
  unique()

# ---- Step 2: Match to master communication events ----
matched_comms_df <- other_communications_df %>%
  filter(event_id %in% event_ids_to_extract)

# ---- Step 3: Prepare data for plotting ----
matched_comms_df_for_plot <- matched_comms_df %>%
  mutate(
    timestamp = as.POSIXct(timestamp),
    comm_date = as.Date(timestamp),
    comm_time_of_day = hms::as_hms(format(timestamp, "%H:%M:%S")),
    sender_sub_type = factor(sender_sub_type, levels = c("Person", "Vessel", "Organization", "Location")),
    communicating_pair_sorted = paste(pmin(sender_name, recipient_name), pmax(sender_name, recipient_name), sep = " & ")
  )

# ---- Step 4: Add tooltip labels ----
plot_data <- matched_comms_df_for_plot %>%
  mutate(
    wrapped_content = str_wrap(content, width = 50),
    tooltip_text = paste0(
      "<b>Date:</b> ", comm_date, "<br>",
      "<b>Time:</b> ", format(comm_time_of_day, "%H:%M:%S"), "<br>",
      "<b>Event ID:</b> ", event_id, "<br><br>",
      "<b>From:</b> ", sender_name, "<br>",
      "<b>To:</b> ", recipient_name, "<br><br>",
      "<b>Content:</b><br>", wrapped_content
    )
  )

# ---- Step 5: Generate timeline plot ----
p <- ggplot(plot_data, aes(x = comm_date, y = comm_time_of_day)) +
  geom_point(aes(
    color = sender_name,
    shape = sender_sub_type,
    text = tooltip_text
  ), show.legend = c(color = TRUE, shape = FALSE), size = 2, alpha = 0.7) +

  scale_shape_manual(values = c(
    "Person" = 16,
    "Vessel" = 17,
    "Organization" = 15,
    "Location" = 18
  )) +

  scale_y_time(
    limits = hms::as_hms(c("08:00:00", "14:00:00")),
    breaks = hms::as_hms(c("08:00:00", "09:00:00", "10:00:00", "11:00:00", "12:00:00", "13:00:00", "14:00:00")),
    labels = c("08:00", "09:00", "10:00", "11:00", "12:00", "13:00", "14:00")
  ) +

  scale_x_date(
    date_breaks = "1 day",
    date_labels = "%d %b"
  ) +

  facet_wrap(~ sender_sub_type, ncol = 1, scales = "fixed") +

  labs(
    title = "Nadia's 3-hop Communications Timeline (Sender Perspective)",
    x = "Date",
    y = "Time of Day",
    color = "Sender"
  ) +

  theme_grey() +
  theme(
    axis.text.y = element_text(size = 6),
    axis.title.y = element_text(size = 7),
    axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 10), size = 7),
    panel.spacing = unit(0.5, "lines"),
    strip.text = element_text(size = 8, face = "bold"),
    legend.position = "bottom",
    legend.text = element_text(size = 6),
    legend.title = element_text(size = 7)
  )

# ---- Step 6: Convert to interactive plot ----
ggplotly(p, tooltip = "text")

```

## **4.5 Discussion/Interpretation (1 & 3 hop data):**

There were certain questions we posted to ourselves and came out with the answers.

### 4.5.1 The Community and Ego Network:

#### Question and Answer Analysis

+--------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Question                                                                                                                                                     | Answer                                                                                                                                                                                                  |
+:=============================================================================================================================================================+:========================================================================================================================================================================================================+
| Who were Nadia’s direct communication contacts (1-hop degree centrality)? Are any of them known to be suspicious or involved in illicit activities?          | From the thicker width in the Ego network, it appeared that Nadia often communicated with **Liam**, **Elise**, and **Davis**.                                                                           |
|                                                                                                                                                              |                                                                                                                                                                                                         |
|                                                                                                                                                              | Liam appeared to be The **Middleman** within Nadia’s direct community from the Louvain Community Network.                                                                                               |
|                                                                                                                                                              |                                                                                                                                                                                                         |
|                                                                                                                                                              | From the filtered table on suspicious relationships, **Elise**, **Liam**, **EcoVigil**, **Sentinel**, **Oceanus City Council**, and **V. Miesel Shipping** were noted to have suspicious relationships. |
|                                                                                                                                                              |                                                                                                                                                                                                         |
|                                                                                                                                                              | Their conversations were the area of focus to uncover their roles, relationships and identities.                                                                                                        |
+--------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Were there any other ‘Event’ or ‘Relationship’ nodes directly connected to Nadia in this communication network that hinted at suspicious people/ activities? | Based on information from question 2, **Rodriguez** was previously involved in **mining activities** that affected the environment. ‘**Mining**’ as a topic and his conversations would be tracked.     |
+--------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+

### 4.5.2 The Communication Timeline and Content:

In the `nadia_full_communications_timeline` table, the actual content of her direct two-way communications were investigated over the course of 9 days. There were certain suspicious entities, keywords, coded language, or unusual topics detected that were suspicious. We have tabled out the segmented suspicious and non-suspicious entities for investigation and elimination.

::: panel-tabset
### Not in the Network but Mentioned in the Content

+-----------------+------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+
| Entity          | Form of Subject Matter | Rationale                                                                                                                                                                                         | Event ID      |
+=================+========================+===================================================================================================================================================================================================+===============+
| Nemo Reef       | Location               | Likely conservation area which was picked by the characters for illicit activities.                                                                                                               | 331, 943      |
+-----------------+------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+
| Permit #CR-7844 | Item                   | Likely a permit to show tourism activity as a cover for suspicious activities. Rodriguez is likely linked to vessels Mako, Neptune, and Remora operating under this permit with a tourism facade. | 582, 847, 805 |
+-----------------+------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+
| EcoVigil        | Vessel                 | EcoVigil will likely affect Nadia's operations when they use their ROV. Nadia recommended to V. Miesel to accelerate the planned operation. They were likely working for different sides.         | 753, 847      |
+-----------------+------------------------+---------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+---------------+

### Suspicious Entity

+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| Suspicious Entity                    | Sub Type     | Community | Rationale                                                                                                                                       | Event ID           |
+======================================+==============+===========+=================================================================================================================================================+====================+
| Haacklee Harbor                      | Location     | 2         | Nadia's communication to Haacklee Harbor is suspicious when she wanted the documents destroyed and the special corridor to Nemo Reef cancelled. | 331                |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| Liam aka The Middleman               | Person       | 2         | Nadia wanted him to double his usual fee to ensure Harbor Master remains cooperative. Identity revealed through:                                | 529, 795, 847      |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| Davis                                | Person       | 1         | Nadia told him to create a clean paper trail. She will provide permits.                                                                         | 521                |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| Elise aka Mrs. Money                 | Person       | 1         | Nadia warned Elise that conservation vessels might complicate their operation. Identity revealed through:                                       | 708, 528, 538, 677 |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| Rodriguez aka Small Fry              | Person       | 1         | Linked to Mako, which is operating under a permit with a tourism facade.                                                                        | 805                |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| Remora                               | Vessel       | 1         | Remora reported a tourism facade to Nadia and planned underwater lighting placements in Nemo Reef while monitoring conservation vessels.        | 943                |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| Neptune                              | Vessel       | 1         | Nadia told Neptune to stay under the radar.                                                                                                     | 538                |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| V. Miesel HQ                         | Organisation | 1         | Organisation was aware of the suspicious permit and The Middleman.                                                                              | 846, 847           |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+
| Sailor Shifts Team aka Glitters Team | Organisation | 1         | Nadia provided crew members for the setup related to the permit.                                                                                | 520                |
+--------------------------------------+--------------+-----------+-------------------------------------------------------------------------------------------------------------------------------------------------+--------------------+

### Non Suspicious Entity

+-----------------------+--------------+-----------+--------------------------------------------------------------------------------------------------------------------------+----------+
| Non Suspicious Entity | Sub Type     | Community | Rationale                                                                                                                | Event ID |
+=======================+==============+===========+==========================================================================================================================+==========+
| Oceanus City Council  | Organisation | 2         | Oceanus City Council as a whole is not suspicious as an organisation as Liam stated this organisation suspected nothing. | 535      |
+-----------------------+--------------+-----------+--------------------------------------------------------------------------------------------------------------------------+----------+
| Sentinel              | Vessel       | 2         | Sentinel Vessel suspected ulterior motives as the water quality was fine.                                                | 677      |
+-----------------------+--------------+-----------+--------------------------------------------------------------------------------------------------------------------------+----------+
| Marlin                | Vessel       | 2         | Marlin inquired about unusual vessel routes near eastern shoals, Nadia and Davis might need to address this.             | 584      |
+-----------------------+--------------+-----------+--------------------------------------------------------------------------------------------------------------------------+----------+
:::

## **4.6 Querying Keywords**

Based on our knowledge, we decided to connect to external information. We used knowledge from Nadia's current network and communication with keyword search of our queries.

### 4.6.1 Plotted Timeline (Word Query: Permit related)

```{r}
#| code-fold: true
#| code-summary: "Show the code"

# -- Step 1: Define keywords
keywords <- c("permit", "1045", "7844")
pattern <- paste0("\\b(", paste(keywords, collapse = "|"), ")\\b")

# -- Step 2: Filter messages with keyword match (case-insensitive)
keyword_matches_df <- other_communications_df %>%
  mutate(content_lower = tolower(content)) %>%
  filter(str_detect(content_lower, pattern))

# -- Step 3: Extract and annotate keyword matches
plot_data <- keyword_matches_df %>%
  mutate(
    matched_keywords = str_extract_all(content_lower, pattern),
    timestamp = suppressWarnings(as.POSIXct(timestamp)),
    comm_date = as.Date(timestamp),
    comm_time_of_day = suppressWarnings(hms::as_hms(format(timestamp, "%H:%M:%S"))),
    wrapped_content = str_wrap(content, width = 50)
  ) %>%
  unnest(matched_keywords) %>%
  mutate(
    matched_keywords = recode(matched_keywords,
      "permit" = "Permit",
      "1045" = "# 1045",
      "7844" = "# 7844"
    ),
    tooltip_text = paste0(
      "<b>Date:</b> ", comm_date,
      "<br><b>Time:</b> ", format(comm_time_of_day, "%H:%M:%S"),
      "<br><b>Event ID:</b> ", event_id,
      "<br><b>Content:</b><br>", wrapped_content
    )
  )

# -- Step 4: Plot timeline
p <- ggplot(plot_data, aes(x = comm_date, y = comm_time_of_day)) +
  geom_point(aes(
    color = matched_keywords,
    shape = sender_sub_type,
    text = tooltip_text,
    group = matched_keywords
  ), size = 2.5, alpha = 0.7, show.legend = TRUE) +
  scale_shape_manual(values = c(
    "Person" = 16,
    "Vessel" = 17,
    "Organization" = 15,
    "Location" = 18
  )) +
  facet_wrap(~ matched_keywords, ncol = 1, scales = "fixed") +
  scale_y_time(
    limits = hms::as_hms(c("08:00:00", "13:00:00")),
    breaks = hms::as_hms(c("08:00:00", "09:00:00", "10:00:00", "11:00:00", "12:00:00", "13:00:00")),
    labels = c("08:00", "09:00", "10:00", "11:00", "12:00", "13:00")
  ) +
  scale_x_date(date_breaks = "1 day", date_labels = "%d %b") +
  labs(
    title = "Interactive Timeline: Keyword Mentions by Day and Time",
    x = "Date",
    y = "Time of Day",
    shape = "Sender Type",
    color = "Keyword"
  ) +
  theme_grey() +
  theme(
    axis.text.y = element_text(size = 6),
    axis.title.y = element_text(size = 7),
    axis.ticks.y = element_line(),
    axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 10), size = 7),
    panel.spacing = unit(0.5, "lines"),
    strip.text = element_text(size = 8, face = "bold"),
    legend.position = "bottom",
    legend.text = element_text(size = 6),
    legend.title = element_blank()
  )

# -- Step 5: Convert to plotly
ggplotly(p, tooltip = "text")


```

### 4.6.1.1 Findings in sequential order:

-   There were overlaps as the blue permit also included the red NR-1045 permit and green CR-7844 permit.

```{r}
#| code-fold: true
#| code-summary: "Show the code"

library(reactable)
library(dplyr)
library(stringr)
library(readr) # Used for read_lines

# 1. Prepare data from the text provided
data_text <- "
Date & Time | Event Description
------------|---------------------------------------------------------------------------------------------------------------
2 Oct (12:16pm) | Rodriguez was from the Sailor Shifts Team.
5 Oct (10:54am) | Jensen from City Council approved Nemo Reef permit.
6 Oct (9:57am) | Remora told Sailor Shifts Team that Nadia got Commissioner Torres to sign off the permit.
6 Oct (10:45am) | Mako acknowledged NR-1045 permit to Nemo Reef.
6 Oct (12:33pm) | Mako was lead vessel to Neptune and Remora as authorised by V. Miesel Shipping.
7 Oct (9:40am) | Mako was operating under permit NR-1045 for conservation research.
8 Oct (10:24am) | Mako was operating under V. Miesel's special marine research permit CR-7844 approved by Oceanus City Council.
8 Oct (10:30am) | Mako informed Remora that both of them were operating under permit CR-7844 and have a 5 day deadline.
8 Oct (10:40am) | Remora was approved by Paackland Harbor to operate with extended hours under permit NR-1045.
9 Oct (11:53am) | Mako requesed for additional crew from v Miesel Shipping for the 24hr operations over next 5 days.
11 Oct (6:00am) | Nemo Reef closure mandated by Oceanus City Council.
11 Oct (8:57am) | All research permits must be submitted within 72 hours.
11 Oct (10:05am) | V. Miesel Shipping informed Remora that 30% of her crew to be reassigned to Neptune.
12 Oct (10:01am) | Davis as Captain oversaw crew reallocation.
12 Oct (11:19am) | Nadia secured documentation for CR-7844.
12 Oct (12:52pm) | Harbor closure for 3 days from 13 Oct 06:00.
"

# Parse the data into a data frame
# Use read_lines to handle the multi-line string
data_lines <- read_lines(data_text)

# Remove the header separator line and any empty lines
data_lines <- data_lines[!grepl("^---|===", data_lines) & data_lines != ""]

# The first non-separator line is the header
col_names_raw <- str_split(data_lines[1], "\\|")[[1]]
col_names <- str_trim(col_names_raw)

# The rest are data rows
data_content <- data_lines[-1]

# Create data frame by splitting lines and putting into a tibble
df <- tibble(line = data_content) %>%
  mutate(
    `Date & Time` = str_trim(str_extract(line, "^[^|]+")),
    `Event Description` = str_trim(str_extract(line, "(?<=\\|).+$"))
  ) %>%
  select(`Date & Time`, `Event Description`) # Ensure correct column order and names

# 2. Create the reactable table with desired features

reactable(
  df,
  filterable = TRUE, # Enable column-specific filters (from the tutorial)
  searchable = TRUE, # Enable global search box (from the tutorial)
  paginationType = "numbers", # Display page numbers (corrected from "pages")
  defaultPageSize = 5, # Show 5 rows per page
  showPageSizeOptions = TRUE, # Allow users to change page size
  pageSizeOptions = c(5, 10, 15, 20, 50), # Options for page sizes
  striped = TRUE, # Add alternating row colors (from the tutorial)
  highlight = TRUE, # Highlight row on hover (from the tutorial)
  columns = list(
    `Date & Time` = colDef(
      name = "Date & Time",
      minWidth = 120, # Adjust width to fit content
      align = "left"
    ),
    `Event Description` = colDef(
      name = "Event Description",
      minWidth = 500, # Ensure enough width for event descriptions
      align = "left"
    )
  ),
  # Apply a custom theme for better aesthetics (inspired by the tutorial)
  theme = reactableTheme(
    borderColor = "#dfe2e5",
    stripedColor = "#f6f8fa",
    highlightColor = "#f0f5f9",
    cellPadding = "8px 12px",
    style = list(fontFamily = "Verdana, Geneva, sans-serif", fontSize = "14px"),
    headerStyle = list(
      "&.rt-th:hover" = list(backgroundColor = "#e0e6eb"),
      fontSize = "15px",
      fontWeight = 600,
      color = "#333", # Darker header text for contrast
      background = "#f7f7f7" # Slightly grey background for header
    ),
    rowSelectedStyle = list(backgroundColor = "#e6f2ff", "&:hover" = list(backgroundColor = "#e6f2ff")),
    # Styles for search/filter inputs (from tutorial's theme example)
    searchInputStyle = list(width = "100%", margin = "5px 0", padding = "5px"),
    filterInputStyle = list(width = "100%", margin = "2px 0", padding = "4px")
  )
)
```

-   Since there were little communications on 13 Oct, we looked into other word queries.

-   Using information obtained from question 2 and 4, we had in mind certain keywords to query for.

### 4.6.2 Plotted Timeline (Word Query: Music Video Related)

```{r}
#| code-fold: true
#| code-summary: "Show the code"
library(dplyr)
library(stringr)
library(ggplot2)
library(plotly)
library(hms)
library(tidyr)

# -- Step 1: Define keywords
keywords <- c("mine", "mining", "music video", "lighting", "reef operation")
pattern <- paste0("\\b(", paste(keywords, collapse = "|"), ")\\b")

# -- Step 2: Filter messages
search_target_content <- tolower(other_communications_df$content)

keyword_matches_df <- other_communications_df %>%
  filter(str_detect(search_target_content, pattern))

# -- Step 3: Extract keywords
plot_data <- keyword_matches_df %>%
  mutate(matched_keywords = str_extract_all(tolower(content), pattern)) %>%
  unnest(matched_keywords) %>%
  mutate(matched_keywords = str_to_title(matched_keywords)) %>%
  arrange(matched_keywords, timestamp) %>%
  mutate(
    timestamp = as.POSIXct(timestamp),
    comm_date = as.Date(timestamp),
    comm_time_of_day = hms::as_hms(format(timestamp, "%H:%M:%S")),
    wrapped_content = str_wrap(content, width = 50),
    tooltip_text = paste0(
      "<b>Date:</b> ", comm_date,
      "<br><b>Time:</b> ", comm_time_of_day,
      "<br><b>Event ID:</b> ", event_id,
      "<br><b>From:</b> ", sender_name,
      "<br><b>To:</b> ", recipient_name,
      "<br><b>Content:</b><br>", wrapped_content
    )
  )

# -- Step 4: Plot
p <- ggplot(plot_data, aes(x = comm_date, y = comm_time_of_day)) +
  geom_point(aes(
    color = matched_keywords,
    shape = sender_sub_type,
    text = tooltip_text,
    group = matched_keywords  # ensures matched_keywords is in layer
  ), size = 2.5, alpha = 0.7, show.legend = TRUE) +
  scale_shape_manual(values = c(
    "Person" = 16,
    "Vessel" = 17,
    "Organization" = 15,
    "Location" = 18
  )) +
  facet_wrap(~ matched_keywords, ncol = 1, scales = "fixed") +
  scale_y_time(
    limits = hms::as_hms(c("08:00:00", "13:00:00")),
    breaks = hms::as_hms(c("08:00:00", "09:00:00", "10:00:00", "11:00:00", "12:00:00", "13:00:00")),
    labels = c("08:00", "09:00", "10:00", "11:00", "12:00", "13:00")
  ) +
  scale_x_date(date_breaks = "1 day", date_labels = "%d %b") +
  labs(
    title = "Interactive Timeline: Keyword Mentions by Day and Time",
    x = "Date",
    y = "Time of Day",
    shape = "Sender Type",
    color = "Keyword"
  ) +
  theme_grey() +
  theme(
    axis.text.y = element_text(size = 6),
    axis.title.y = element_text(size = 7),
    axis.ticks.y = element_line(),
    axis.text.x = element_text(size = 6, angle = 45, hjust = 1),
    axis.title.x = element_text(margin = margin(t = 10), size = 7),
    panel.spacing = unit(0.5, "lines"),  # Applies to both x and y spacing
    strip.text = element_text(size = 8, face = "bold"),
    legend.position = "bottom",
    legend.text = element_text(size = 6),
    legend.title = element_blank()
  )

# -- Step 5: Convert to plotly
ggplotly(p, tooltip = "text")
```

### 4.6.2.1 Findings through Questions & Answers:

#### **Question and Answer Analysis**

+------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| **Question**                                                                                                                 | **Answer**                                                                                                                                                                                                                                                                                                                               |
+==============================================================================================================================+==========================================================================================================================================================================================================================================================================================================================================+
| Which vessel was the suspicious permit #CR-7844 prepared for?                                                                | From question 2 and 4, we know this is V. Miesel's Marine Research Permit, and prepared for Mako (lead vessel), Neptune, and Remora.                                                                                                                                                                                                     |
|                                                                                                                              |                                                                                                                                                                                                                                                                                                                                          |
| (See 4.6.1.1)                                                                                                                |                                                                                                                                                                                                                                                                                                                                          |
+------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| What suspicious activity was performed at Nemo Reef? Which day was it?                                                       | 14 Oct 2040 for a music video production.                                                                                                                                                                                                                                                                                                |
|                                                                                                                              |                                                                                                                                                                                                                                                                                                                                          |
| (See 4.6.2)                                                                                                                  |                                                                                                                                                                                                                                                                                                                                          |
+------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Why is underwater lighting placement needed at Nemo Reef?                                                                    | For a music video production.                                                                                                                                                                                                                                                                                                            |
|                                                                                                                              |                                                                                                                                                                                                                                                                                                                                          |
| (See 4.6.2)                                                                                                                  |                                                                                                                                                                                                                                                                                                                                          |
+------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| What were the expedited approvals and secretive logistics?                                                                   | Permits for Nemo Reef through NR-1045 and CR-788 were expedited. The secretive logistics were the crates and equipment on the vessels for the music video production.                                                                                                                                                                    |
|                                                                                                                              |                                                                                                                                                                                                                                                                                                                                          |
| (See 4.6.1 and 4.6.2)                                                                                                        |                                                                                                                                                                                                                                                                                                                                          |
+------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Who were the high-level Oceanus officials, Sailor Shift’s team, local influential families, and local conservationist group? | **Oceanus Officials**: Commissioner Blake, Commissioner Torres, Council Knowles, The Middleman, Jensen, Liam Thorne                                                                                                                                                                                                                      |
|                                                                                                                              |                                                                                                                                                                                                                                                                                                                                          |
| (Various Ids)                                                                                                                | **Sailor Shift’s Team**: Boss, Council Knowles, Davis, Glitters Team, Liam Thorne, Mako, Mrs. Money, Nadia, Neptune, Remora, Rodriguez, Sam, Samantha Blake, Small Fry, The Accountant, The Intern, The Middleman                                                                                                                        |
|                                                                                                                              |                                                                                                                                                                                                                                                                                                                                          |
|                                                                                                                              | **Local Influential Families**: Council Knowles, V. Miesel Shipping                                                                                                                                                                                                                                                                      |
|                                                                                                                              |                                                                                                                                                                                                                                                                                                                                          |
|                                                                                                                              | **Local Conservationist Group**: Defender, EcoVigil, Green Guardians, Horizon, Kelly, Reef Guardians, Seawatch, Sentinel, The Lookout                                                                                                                                                                                                    |
+------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
| Was the music video production activity legal?                                                                               | There was no environmental damage or mining involved in the music production. However, an environmental assessment was not conducted prior. Clepper may assess that his suspicions about Nadia Conti's illicit activity may not be straightforward and could depend on whether an assessment was mandatory before commercial activities. |
|                                                                                                                              |                                                                                                                                                                                                                                                                                                                                          |
| (Id 979)                                                                                                                     |                                                                                                                                                                                                                                                                                                                                          |
+------------------------------------------------------------------------------------------------------------------------------+------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------+
